---
title: "Fish Eating Bats Gene Loss"
author: "Anastasiya Stepanenko"
format: 
  html:
    toc: true
    html-math-method: katex
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    toc-location: left
    code-fold: true
    code-tools: true
    theme: lumen
    embed-resources: true
editor: visual
---

```{r}
#| message: false
#| warning: false
library(ggplot2); theme_set(theme_bw())
library(ggVennDiagram)
library(gprofiler2)
library(ggpubr)
library(ape)
library(phytools)
library(ggtree)
library(tidytree)
library(cowplot)
library(tidyverse)
library(reshape)
library(phangorn)
library(stringr)
library(kableExtra)
library(stringr)
library(egg)
library(org.Hs.eg.db)
library(ggnewscale)
library(treeio)
library(ggvenn)

`%notin%` <- Negate(`%in%`)
`%+=%` = function(e1,e2) eval.parent(substitute(e1 <- e1 + e2))
```

## Diets of bats

Illustration of the diets of bats from Wilman et al., 2014.

```{r, fig.width = 15, fig.height = 5}
#| message: false
#| warning: false
bat_families <- c(
    "Pteropodidae",          # Old World fruit bats
    "Rhinopomatidae",        # Mouse-tailed bats
    "Craseonycteridae",      # Hog-nosed bat
    "Megadermatidae",        # False-vampires
    "Rhinonycteridae",       # Trident bats
    "Hipposideridae",        # Old World leaf-nosed bats
    "Rhinolophidae",         # Horseshoe bats
    "Nycteridae",            # Slit-faced bats
    "Emballonuridae",        # Sheath-tailed bats
    "Myzopodidae",           # Madagascar sucker-footed bats
    "Mystacinidae",          # New Zealand short-tailed bats
    "Thyropteridae",         # Disk-winged bats
    "Furipteridae",          # Smoky and thumbless bats
    "Noctilionidae",         # Bulldog bats
    "Mormoopidae",           # Ghost-faced bats
    "Phyllostomidae",        # New World leaf-nosed bats
    "Natalidae",             # Funnel-eared bats
    "Molossidae",            # Free-tailed bats
    "Miniopteridae",         # Long-fingered bats
    "Cistugidae",            # Wing-gland bats
    "Vespertilionidae"       # Plain-nosed bats
)

diet_df = read.csv("data_from_wilman/MamFuncDat.txt", sep="\t")
diet_df = diet_df[diet_df$MSWFamilyLatin %in% bat_families, ]
rownames(diet_df) = diet_df$Scientific
diet_df = diet_df[, c(4:13)]

diet_df_hm <- melt(as.matrix(diet_df))
colnames(diet_df_hm) <- c("Species", "Diet", "Value")
ggplot(diet_df_hm, aes(x = Species, y = Diet, fill = Value)) +
  geom_tile() +
  scale_fill_gradient2(high="red", mid= "blue", low="white", midpoint = 50) +
  theme(axis.text.x=element_blank())
```

## Ariadna's Tree

This is a tree we will be using to look at the gene losses and selection screen. Two foreground species are marked red. \[to be cited\]

```{r, fig.width = 12, fig.height = 13}
setwd("/home/ana/Documents/loss")
tree <- read.tree("tree21fam0.tree")
table_bats <- read.csv("Yangochiroptera77.csv")
synonyms_df <- data.frame(
  old = c(table_bats$Assembly),
  new = c(table_bats$ScientificName)
)
rownames(table_bats) = table_bats$Assembly
tree <- drop.tip(tree, tree$tip.label[tree$tip.label %notin% c(rownames(table_bats), "hg38")])
write.tree(tree, file='tree_for_selection_screen.tree')
tree <- read.tree("Ariadna_21Famout_Yango77_noNA_nodelab.tre")
tree$edge.length <- rep(1, length(tree$edge.length))
tree$label = rep("background", nrow(tree$edge)+1)
tree$label[MRCA(tree, "HLnocLep2")] = tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
table_bats = table_bats[, c("Arthropods", "Blood", "Terrestrial.vertebrates", "Fish", "Leaves.and.flower.pieces", "Pollen.and.nectar", "Fruit")]
table_bats = as.data.frame(table_bats)
diets = c("Arthropods", "Blood", "Terrestrial.vertebrates", 
          "Fish", "Leaves.and.flower.pieces", "Pollen.and.nectar", "Fruit", "Seed")
diet.states = c("Absent" = 0, "Complementary" = 1, "Predominant" = 2, "Strict" = 3)
state.color = c("#d2dae1", "#6baed6", "#08519c", "black")

renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
rownames(table_bats) = synonyms_df[synonyms_df$old %in% rownames(table_bats),]$new

tree_for_plot = ggplot(renamed_tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE, fontface = "italic", size=7)#+hexpand(2) 
gheatmap(tree_for_plot, table_bats, offset=18, width = 0.5, color = "black",, colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1) + vexpand(-1)  + vexpand(-1)
```

## Gene losses

```{r, fig.width = 12, fig.height = 2.5}
#| message: false
#| warning: false
gene_loss_full = read.csv("lost_genes_with_myoviv5.txt", sep="\t", row.names = 1, header = T) %>% as.data.frame()

myoviv_3_intersection_L = gene_loss_full[,c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLmyoViv5")]
myoviv_3_intersection_L = myoviv_3_intersection_L[rowMeans(myoviv_3_intersection_L == "L") > 0,]
write.table(myoviv_3_intersection_L, "myoViv_gene_losses.tsv", sep="\t", row.names = T)
print(myoviv_3_intersection_L[myoviv_3_intersection_L$HLmyoViv1 == "I" & myoviv_3_intersection_L$HLmyoViv3 == "L",])
gene.states = c("FI", "I", "PI", "L", "UL", "M", "PM", "PG", "N")
gene.colors = c("azure2", "grey", "steelblue", "#bd0026", "#fd8d3c", "yellow","#ffffb2","grey20", "white")
myoviv_3_intersection_L_for_heat <- melt(as.matrix(myoviv_3_intersection_L))
colnames(myoviv_3_intersection_L_for_heat) <- c("y", "x", "value")
ggplot(myoviv_3_intersection_L_for_heat, aes(x = x, y = y, fill = value)) +
  geom_tile() + coord_flip() + xlab("Assembly") + ylab("Gene") +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
  theme(axis.text.x=element_blank())
```

```{r, fig.width = 20, fig.height = 10}
#| warning: false
#| error: false
#| message: false
gene_loss_full <- gene_loss_full[, !(colnames(gene_loss_full) %in% c("HLmyoViv2", "HLmyoViv3"))]
myoviv_L_intersection <- list(HLmyoViv1 = rownames(gene_loss_full[gene_loss_full$HLmyoViv1 == "L",]),
                              #HLmyoViv2 = rownames(gene_loss_full[gene_loss_full$HLmyoViv2 == "L",]),
                              #HLmyoViv3 = rownames(gene_loss_full[gene_loss_full$HLmyoViv3 == "L",]),
                              HLmyoViv5 = rownames(gene_loss_full[gene_loss_full$HLmyoViv5 == "L",]))
myoviv1_L_uniq_status_myoviv5 <- gene_loss_full[(gene_loss_full$HLmyoViv1 == "L") & (gene_loss_full$HLmyoViv5 != "L"),]
myoviv5_L_uniq_status_myoviv1 <- gene_loss_full[(gene_loss_full$HLmyoViv5 == "L") & (gene_loss_full$HLmyoViv1 != "L"),]

myoviv_L_UL_intersection <- list(HLmyoViv1 = rownames(gene_loss_full[gene_loss_full$HLmyoViv1 %in% c("L", "UL"),]),
                                 #HLmyoViv2 = rownames(gene_loss_full[gene_loss_full$HLmyoViv2 %in% c("L", "UL"),]),
                                 #HLmyoViv3 = rownames(gene_loss_full[gene_loss_full$HLmyoViv3 %in% c("L", "UL"),]),
                                 HLmyoViv5 = rownames(gene_loss_full[gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]))
myoviv1_L_UL_uniq_status_myoviv5 <- gene_loss_full[(gene_loss_full$HLmyoViv1 %in% c("L", "UL")) & (gene_loss_full$HLmyoViv5 %notin% c("L", "UL")),]
myoviv5_L_UL_uniq_status_myoviv1 <- gene_loss_full[(gene_loss_full$HLmyoViv5 %in% c("L", "UL")) & (gene_loss_full$HLmyoViv1 %notin% c("L", "UL")),]

noclep_L_intersection <- list(HLnocLep1 = rownames(gene_loss_full[gene_loss_full$HLnocLep1 == "L",]),
                              HLnocLep2 = rownames(gene_loss_full[gene_loss_full$HLnocLep2 == "L",]))
noclep1_L_uniq_status_noclep2 <- gene_loss_full[(gene_loss_full$HLnocLep1 == "L") & (gene_loss_full$HLnocLep2 != "L"),]
noclep2_L_uniq_status_noclep1 <- gene_loss_full[(gene_loss_full$HLnocLep2 == "L") & (gene_loss_full$HLnocLep1 != "L"),]

noclep_L_UL_intersection <- list(HLnocLep1 = rownames(gene_loss_full[gene_loss_full$HLnocLep1 %in% c("L", "UL"),]),
                                 HLnocLep2 = rownames(gene_loss_full[gene_loss_full$HLnocLep2 %in% c("L", "UL"),]))
noclep1_L_UL_uniq_status_noclep2 <- gene_loss_full[(gene_loss_full$HLnocLep1 %in% c("L", "UL")) & (gene_loss_full$HLnocLep2 %notin% c("L", "UL")),]
noclep2_L_UL_uniq_status_noclep1 <- gene_loss_full[(gene_loss_full$HLnocLep2 %in% c("L", "UL")) & (gene_loss_full$HLnocLep1 %notin% c("L", "UL")),]

# 2D Venn diagram
p1 <- ggVennDiagram(myoviv_L_intersection) + ggtitle("Myotis vivesi L") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p1_1 <- ggplot(myoviv1_L_uniq_status_myoviv5, aes(x=factor(HLmyoViv5)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLmyoViv1 only")
p1_2 <- ggplot(myoviv5_L_uniq_status_myoviv1, aes(x=factor(HLmyoViv1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLmyoViv5 only")
p2 <- ggVennDiagram(myoviv_L_UL_intersection) + ggtitle("Myotis vivesi L+UL") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p2_1 <- ggplot(myoviv1_L_UL_uniq_status_myoviv5, aes(x=factor(HLmyoViv5)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLmyoViv1 only")
p2_2 <- ggplot(myoviv5_L_UL_uniq_status_myoviv1, aes(x=factor(HLmyoViv1)))+geom_bar(stat="count",)+theme_minimal()+ggtitle("L+UL HLmyoViv5 only")
p3 <- ggVennDiagram(noclep_L_intersection) + ggtitle("Noctilio leporinus L") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p3_1 <- ggplot(noclep1_L_uniq_status_noclep2, aes(x=factor(HLnocLep2)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLnocLep1 only")
p3_2 <- ggplot(noclep2_L_uniq_status_noclep1, aes(x=factor(HLnocLep1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLnocLep2 only")
p4 <- ggVennDiagram(noclep_L_UL_intersection) + ggtitle("Noctilio leporinus L+UL") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p4_1 <- ggplot(noclep1_L_UL_uniq_status_noclep2, aes(x=factor(HLnocLep2)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLnocLep1 only")
p4_2 <- ggplot(noclep2_L_UL_uniq_status_noclep1, aes(x=factor(HLnocLep1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLnocLep2 only")

#ggarrange(p1, p1_1, p1_2, p2, p2_1, p2_2, p3, p3_1, p3_2, p4, p4_1, p4_2, nrow = 4)
ggarrange(p1, p2, p3, p4, p1_1, p2_1, p3_1, p4_1, p1_2, p2_2, p3_2, p4_2, nrow = 3, heights = c(2,1,1))
#, width=0.7, fill="steelblue"
```

::: panel-tabset
### Myotis vivesi

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
all_species = colnames(gene_loss_full)
gene_loss_viv_table = gene_loss_full[gene_loss_full$HLmyoViv1 %notin% c("I", "FI") & gene_loss_full$HLmyoViv5 == "L",]# & gene_loss_full$HLmyoViv3 == "L" & gene_loss_full$HLmyoViv5 == "L",]
gene_loss_lep_table = gene_loss_full[gene_loss_full$HLnocLep1 %notin% c("I", "FI") & gene_loss_full$HLnocLep2 == "L",]#, "UL"),]

gene_L_UL_viv_table = gene_loss_full[gene_loss_full$HLmyoViv1 %notin% c("I", "FI") & gene_loss_full$HLmyoViv5 %in% c("L", "UL"),] #& gene_loss_full$HLmyoViv3 %in% c("L", "UL")  & gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]
gene_L_UL_lep_table = gene_loss_full[gene_loss_full$HLnocLep1 %notin% c("I", "FI") & gene_loss_full$HLnocLep2 %in% c("L", "UL"),]#, "UL"),]
#list_lost_sameasviv = list_lost_sameaslep = c()
#for (species in all_species) {
#  list_lost_sameasviv = c(list_lost_sameasviv, nrow(gene_loss_viv_table[gene_loss_viv_table[,species] == "L",]))
#  list_lost_sameaslep = c(list_lost_sameaslep, nrow(gene_loss_lep_table[gene_loss_lep_table[,species] == "L",]))
#}
#gene_loss_viv = data.frame(label=colnames(gene_loss_viv_table), count=max(list_lost_sameasviv) - list_lost_sameasviv)
#gene_loss_lep = data.frame(label=colnames(gene_loss_lep_table), count=max(list_lost_sameaslep) - list_lost_sameaslep)
#tree$loss_viv = tree$loss_lep = rep(NA, nrow(tree$edge)+1)
#max_lost_viv = nrow(gene_loss_viv_table)
#max_lost_lep = nrow(gene_loss_lep_table)

#for (tip in c(tree$tip.label)) {
#  if (tip %in% all_species){
#    tip_number = MRCA(tree, tip)
#    tree$loss_viv[tip_number] = gene_loss_viv[gene_loss_viv$label == tip,]$count
#    tree$loss_lep[tip_number] = gene_loss_lep[gene_loss_lep$label == tip,]$count
#  }
#}

losses_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_loss_viv_table)))
losses_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_loss_lep_table)))

L_UL_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_L_UL_viv_table)))
L_UL_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_L_UL_lep_table)))


for (label1 in all_species){
  for (label2 in all_species) {
    label_in_tree = paste0(label1, "_", label2)
    if (label_in_tree %in% c(tree$node.label)) {
      node_number = MRCA(tree, label_in_tree)
      tips = tree$tip.label[unlist(Descendants(tree, node_number, type = c("tips")))]
      if ("HLmyoViv5" %in% tips) {
        if (length(tips) < 4) {
          losses_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_viv_table) %in% 
                                                            c(rownames(gene_loss_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
          L_UL_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_viv_table) %in% 
                                                            c(rownames(gene_L_UL_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
        }
        else {
          losses_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_loss_viv_table) %in% 
                                                            rownames(gene_loss_viv_table[(rowMeans(gene_loss_viv_table[,tips[tips != "HLmyoViv5"]] == "I") +
                                                                                            rowMeans(gene_loss_viv_table[,tips[tips != "HLmyoViv5"]] == "FI")) >= 0.9,])))
          L_UL_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_L_UL_viv_table) %in% 
                                                            rownames(gene_L_UL_viv_table[(rowMeans(gene_L_UL_viv_table[,tips[tips != "HLmyoViv5"]] == "I") +
                                                                                            rowMeans(gene_L_UL_viv_table[,tips[tips != "HLmyoViv5"]] == "FI")) >= 0.9,])))
        }
      }
      if ("HLnocLep2" %in% tips) {
        if (length(tips) < 3) {
          losses_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_lep_table) %in% 
                                                            c(rownames(gene_loss_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
          L_UL_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_lep_table) %in% 
                                                            c(rownames(gene_L_UL_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
        }
        else {
          losses_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_lep_table) %in% 
                                                            rownames(gene_loss_lep_table[(rowMeans(gene_loss_lep_table[,tips[tips != "HLnocLep2"]] == "I") +
                                                                                            rowMeans(gene_loss_lep_table[,tips[tips != "HLnocLep2"]] == "FI")) >= 0.9,])))
          L_UL_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_lep_table) %in% 
                                                            rownames(gene_L_UL_lep_table[(rowMeans(gene_L_UL_lep_table[,tips[tips != "HLnocLep2"]] == "I") +
                                                                                            rowMeans(gene_L_UL_lep_table[,tips[tips != "HLnocLep2"]] == "FI")) >= 0.9,])))
        }
      }
    }
  }
}
losses_by_background_viv = losses_by_background_viv[-c(1),order(losses_by_background_viv["node_number",], decreasing = TRUE)]
losses_by_background_lep = losses_by_background_lep[-c(1),order(losses_by_background_lep["node_number",], decreasing = TRUE)]

L_UL_by_background_viv = L_UL_by_background_viv[-c(1),order(L_UL_by_background_viv["node_number",], decreasing = TRUE)]
L_UL_by_background_lep = L_UL_by_background_lep[-c(1),order(L_UL_by_background_lep["node_number",], decreasing = TRUE)]

#ggtree(tree, aes(color=tree$loss_viv)) + scale_color_gradient2(high="blue", mid= "orange", low="gray",
#                                                                midpoint = mean(gene_loss_viv$count),
#                        limits = c(min(tree$loss_viv), max(tree$loss_viv)), 
#                        oob = scales::squish) + 
#  ggtitle("Number of common L/UL with L in HLmyoViv2") +
#  geom_tree() + theme_tree() + geom_tiplab()
```

```{r, fig.width = 14, fig.height = 12}
#| message: false
#| warning: false
losses_by_background_viv = losses_by_background_viv[losses_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
losses_by_background_viv = losses_by_background_viv[order(losses_by_background_viv[,2]),]
losses_by_background_viv = losses_by_background_viv[losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
losses_viv_all_states = gene_loss_viv_table[rownames(losses_by_background_viv), colnames(gene_loss_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
#losses_viv_all_states <- losses_viv_all_states[, tree$tip.label]
gene_symbols = select(org.Hs.eg.db, rownames(losses_viv_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
rownames(losses_viv_all_states) = gene_symbols$SYMBOL
species = synonyms_df[order(match(synonyms_df$old, colnames(losses_viv_all_states))),]
colnames(losses_viv_all_states) = species[synonyms_df$old %in% colnames(losses_viv_all_states),]$new
losses_viv_all_states_for_heat <- melt(as.matrix(losses_viv_all_states))
colnames(losses_viv_all_states_for_heat) <- c("y", "x", "value")
#ggplot(losses_viv_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile(color = "black") +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))
tree$label[MRCA(tree, "HLnocLep2")] = "background"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
tree_viv = ggplot(renamed_tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE, font = "italic", size = 7)
gheatmap(tree_viv, as.data.frame(t(losses_viv_all_states)), offset=6, width = 0.2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
#theme(legend.position="none", axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
  #geom_text(data=as.data.frame(t(losses_viv_all_states)), aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
#df = get_heatmap_column_position(p, by="bottom")
#p + geom_text(data=df, aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_viv_table))
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
gostplot(enrichment.not_same.myoviv, capped = TRUE, interactive = TRUE)
```

```{r, fig.width = 15, fig.height = 12}
#| message: false
#| warning: false
L_UL_by_background_viv = L_UL_by_background_viv[L_UL_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
L_UL_by_background_viv = L_UL_by_background_viv[order(L_UL_by_background_viv[,2]),]
L_UL_by_background_viv = L_UL_by_background_viv[L_UL_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
L_UL_viv_all_states = gene_L_UL_viv_table[rownames(L_UL_by_background_viv), colnames(gene_L_UL_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
gene_symbols = select(org.Hs.eg.db, rownames(L_UL_viv_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
rownames(L_UL_viv_all_states) = gene_symbols$SYMBOL
colnames(L_UL_viv_all_states) = species[synonyms_df$old %in% colnames(L_UL_viv_all_states),]$new
L_UL_viv_all_states_for_heat <- melt(as.matrix(L_UL_viv_all_states))
colnames(L_UL_viv_all_states_for_heat) <- c("y", "x", "value")
#ggplot(L_UL_viv_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile() +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))

gheatmap(tree_viv, as.data.frame(t(L_UL_viv_all_states)), offset=10, width = 1.2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(legend.position="none", axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
enrichment.not_same.myoviv = gost(rownames(L_UL_by_background_viv),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_viv_table))
#enrichment.not_same.myoviv = gost(rownames(L_UL_by_background_viv[rowMeans(L_UL_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
gostplot(enrichment.not_same.myoviv, capped = TRUE, interactive = TRUE)
```

### Noctilio leporinus

```{r, fig.width = 15, fig.height = 12}
#| message: false
#| warning: false
losses_by_background_lep = losses_by_background_lep[losses_by_background_lep[,1] != 0,]
losses_by_background_lep = losses_by_background_lep[order(losses_by_background_lep[,2]),]
losses_by_background_lep = losses_by_background_lep[losses_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
losses_lep_all_states = gene_loss_lep_table[rownames(losses_by_background_lep), colnames(gene_loss_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
gene_symbols = select(org.Hs.eg.db, rownames(losses_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#gene_symbols = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]
rownames(losses_lep_all_states) = gene_symbols$SYMBOL
losses_lep_all_states_for_heat <- melt(as.matrix(losses_lep_all_states))
colnames(losses_lep_all_states_for_heat) <- c("y", "x", "value")
#ggplot(losses_lep_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile() +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))
#tree_plot = ggplot(tree, aes(color=tree$label)) + scale_color_manual(values=c("foreground"="#d1182a", "background"="#555555")) + 
#  geom_tree() + theme_tree() + geom_tiplab(align=TRUE)
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv5")] = "background"
tree_lep = ggplot(tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE)
gheatmap(tree_lep, as.data.frame(t(losses_lep_all_states)), offset=4, width = 0.8, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
  #geom_text(data=as.data.frame(t(losses_viv_all_states)), aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
#df = get_heatmap_column_position(p, by="bottom")
#p + geom_text(data=df, aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
enrichment.not_same.noclep = gost(rownames(losses_by_background_lep),#[rowMeans(losses_by_background_lep == 1) == 1,]),
                                  evcodes = TRUE, custom_bg = rownames(gene_loss_full))
#enrichment.not_same.noclep = gost(c("POLM", "GPRC6A", "TUBA8", "F8", "DHRS7", "C22orf15", "MRGPRX3", "KRTAP5-4", "CHMP4A", "DGLUCY", "SMCO1", "B3GNT4", "ALDH1B1", "DLX4", "APOBEC4", "PCDHB14", "RLN2", "RLN1", "ANKRD37"), evcodes = TRUE)
gostplot(enrichment.not_same.noclep, capped = TRUE, interactive = TRUE)
#enrichment_both = gost(c("PLEKHN1", "MN1", "H4C9", "ZFP36", "KLF13", "STX10", "H2AC11", "LCMT2", "NTHL1", "JUNB", "HCN3", "POLM", "GPRC6A", "TUBA8", "F8", "DHRS7", "C22orf15", "MRGPRX3", "KRTAP5-4", "CHMP4A", "DGLUCY", "SMCO1", "B3GNT4", "ALDH1B1", "DLX4", "APOBEC4", "PCDHB14", "RLN2", "RLN1", "ANKRD37"), evcodes = TRUE)
#https://www.informatics.jax.org/vocab/hp_ontology/HP:0031816
```

ENSG00000108813 - L

```{r, fig.width = 17, fig.height = 14}
#| message: false
#| warning: false
L_UL_by_background_lep = L_UL_by_background_lep[L_UL_by_background_lep[,1] != 0,]
L_UL_by_background_lep = L_UL_by_background_lep[order(L_UL_by_background_lep[,2]),]
L_UL_by_background_lep = L_UL_by_background_lep[L_UL_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
L_UL_lep_all_states = gene_L_UL_lep_table[rownames(L_UL_by_background_lep), colnames(gene_L_UL_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
gene_symbols = select(org.Hs.eg.db, rownames(L_UL_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
rownames(L_UL_lep_all_states) = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]$SYMBOL
gheatmap(tree_lep, as.data.frame(t(L_UL_lep_all_states)), offset=16, width = 8, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
enrichment.not_same.noclep = gost(rownames(L_UL_by_background_lep[L_UL_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]),#[rowMeans(losses_by_background_lep == 1) == 1,]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_lep_table))
#enrichment.not_same.noclep = gost(c("POLM", "GPRC6A", "TUBA8", "F8", "DHRS7", "C22orf15", "MRGPRX3", "KRTAP5-4", "CHMP4A", "DGLUCY", "SMCO1", "B3GNT4", "ALDH1B1", "DLX4", "APOBEC4", "PCDHB14", "RLN2", "RLN1", "ANKRD37"), evcodes = TRUE)
#gostplot(enrichment.not_same.noclep, capped = TRUE, interactive = TRUE)
#enrichment_both = gost(c("PLEKHN1", "MN1", "H4C9", "ZFP36", "KLF13", "STX10", "H2AC11", "LCMT2", "NTHL1", "JUNB", "HCN3", "POLM", "GPRC6A", "TUBA8", "F8", "DHRS7", "C22orf15", "MRGPRX3", "KRTAP5-4", "CHMP4A", "DGLUCY", "SMCO1", "B3GNT4", "ALDH1B1", "DLX4", "APOBEC4", "PCDHB14", "RLN2", "RLN1", "ANKRD37"), evcodes = TRUE)
#https://www.informatics.jax.org/vocab/hp_ontology/HP:0031816
```
:::

## Gene losses TOGA2

```{r, fig.width = 12, fig.height = 2.5}
#| message: false
#| warning: false
gene_loss_full = read.csv("toga2_loss/lost_genes_16072025.txt", sep="\t", row.names = 1, header = T) %>% as.data.frame()
```

```{r, fig.width = 16, fig.height = 8}
#| warning: false
#| error: false
#| message: false
gene_loss_full <- gene_loss_full[, !(colnames(gene_loss_full) %in% c("HLmyoViv2", "HLmyoViv3"))]
gene_loss_full = gene_loss_full[rowMeans(gene_loss_full == "N") != 1,]
genes_for_selection_screen = gene_loss_full[gene_loss_full$HLmyoViv5 %in% c("FI", "I", "UL") & gene_loss_full$HLnocLep2 %in% c("FI", "I", "UL"),]
genes_for_selection_screen = strsplit(rownames(genes_for_selection_screen),"#") %>% lapply(function(x) x[1]) %>% unlist
myoviv_L_intersection <- list(HLmyoViv1 = rownames(gene_loss_full[gene_loss_full$HLmyoViv1 == "L",]),
                              #HLmyoViv2 = rownames(gene_loss_full[gene_loss_full$HLmyoViv2 == "L",]),
                              #HLmyoViv3 = rownames(gene_loss_full[gene_loss_full$HLmyoViv3 == "L",]),
                              HLmyoViv5 = rownames(gene_loss_full[gene_loss_full$HLmyoViv5 == "L",]))

myoviv1_L_uniq_status_myoviv5 <- gene_loss_full[(gene_loss_full$HLmyoViv1 == "L") & (gene_loss_full$HLmyoViv5 != "L"),]
myoviv5_L_uniq_status_myoviv1 <- gene_loss_full[(gene_loss_full$HLmyoViv5 == "L") & (gene_loss_full$HLmyoViv1 != "L"),]

myoviv_L_UL_intersection <- list(HLmyoViv1 = rownames(gene_loss_full[gene_loss_full$HLmyoViv1 %in% c("L", "UL"),]),
                                 #HLmyoViv2 = rownames(gene_loss_full[gene_loss_full$HLmyoViv2 %in% c("L", "UL"),]),
                                 #HLmyoViv3 = rownames(gene_loss_full[gene_loss_full$HLmyoViv3 %in% c("L", "UL"),]),
                                 HLmyoViv5 = rownames(gene_loss_full[gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]))
myoviv1_L_UL_uniq_status_myoviv5 <- gene_loss_full[(gene_loss_full$HLmyoViv1 %in% c("L", "UL")) & (gene_loss_full$HLmyoViv5 %notin% c("L", "UL")),]
myoviv5_L_UL_uniq_status_myoviv1 <- gene_loss_full[(gene_loss_full$HLmyoViv5 %in% c("L", "UL")) & (gene_loss_full$HLmyoViv1 %notin% c("L", "UL")),]

noclep_L_intersection <- list(HLnocLep1 = rownames(gene_loss_full[gene_loss_full$HLnocLep1 == "L",]),
                              HLnocLep2 = rownames(gene_loss_full[gene_loss_full$HLnocLep2 == "L",]))
noclep1_L_uniq_status_noclep2 <- gene_loss_full[(gene_loss_full$HLnocLep1 == "L") & (gene_loss_full$HLnocLep2 != "L"),]
noclep2_L_uniq_status_noclep1 <- gene_loss_full[(gene_loss_full$HLnocLep2 == "L") & (gene_loss_full$HLnocLep1 != "L"),]

noclep_L_UL_intersection <- list(HLnocLep1 = rownames(gene_loss_full[gene_loss_full$HLnocLep1 %in% c("L", "UL"),]),
                                 HLnocLep2 = rownames(gene_loss_full[gene_loss_full$HLnocLep2 %in% c("L", "UL"),]))
noclep1_L_UL_uniq_status_noclep2 <- gene_loss_full[(gene_loss_full$HLnocLep1 %in% c("L", "UL")) & (gene_loss_full$HLnocLep2 %notin% c("L", "UL")),]
noclep2_L_UL_uniq_status_noclep1 <- gene_loss_full[(gene_loss_full$HLnocLep2 %in% c("L", "UL")) & (gene_loss_full$HLnocLep1 %notin% c("L", "UL")),]

# 2D Venn diagram
p1 <- ggVennDiagram(myoviv_L_intersection) + ggtitle("Myotis vivesi L") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p1_1 <- ggplot(myoviv1_L_uniq_status_myoviv5, aes(x=factor(HLmyoViv5)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLmyoViv1 only")+xlab("state in HLmyoViv5")
p1_2 <- ggplot(myoviv5_L_uniq_status_myoviv1, aes(x=factor(HLmyoViv1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLmyoViv5 only")+xlab("state in HLmyoViv1")
p2 <- ggvenn(myoviv_L_UL_intersection, fill_color=c("darkblue", "darkgreen"), show_percentage = F, set_name_size = 10, text_size = 10)# + ggtitle("Myotis vivesi L and UL") + theme(plot.title = element_text(size = 20))
# + coord_flip() + scale_x_continuous(expand = expansion(mult = .3)) 
p2_1 <- ggplot(myoviv1_L_UL_uniq_status_myoviv5, aes(x=factor(HLmyoViv5)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLmyoViv1 only")+xlab("state in HLmyoViv5")+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), plot.title = element_text(size = 14))
p2_2 <- ggplot(myoviv5_L_UL_uniq_status_myoviv1, aes(x=factor(HLmyoViv1)))+geom_bar(stat="count",)+theme_minimal()+ggtitle("L+UL HLmyoViv5 only")+xlab("state in HLmyoViv1")+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), plot.title = element_text(size = 14))
p3 <- ggVennDiagram(noclep_L_intersection) + ggtitle("Noctilio leporinus L") + coord_flip() + scale_x_continuous(expand = expansion(mult = .3))
p3_1 <- ggplot(noclep1_L_uniq_status_noclep2, aes(x=factor(HLnocLep2)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLnocLep1 only")+xlab("state in HLnocLep2")
p3_2 <- ggplot(noclep2_L_uniq_status_noclep1, aes(x=factor(HLnocLep1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L HLnocLep2 only")+xlab("state in HLnocLep1")
p4 <- ggvenn(noclep_L_UL_intersection, fill_color=c("darkblue", "darkgreen"), show_percentage = F, set_name_size = 10, text_size = 10) #+ ggtitle("Noctilio leporinus L and UL") + theme(plot.title = element_text(size = 20))
p4_1 <- ggplot(noclep1_L_UL_uniq_status_noclep2, aes(x=factor(HLnocLep2)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLnocLep1 only")+xlab("state in HLnocLep2")+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), plot.title = element_text(size = 14))
p4_2 <- ggplot(noclep2_L_UL_uniq_status_noclep1, aes(x=factor(HLnocLep1)))+geom_bar(stat="count")+theme_minimal()+ggtitle("L+UL HLnocLep2 only")+xlab("state in HLnocLep1")+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), plot.title = element_text(size = 14))

#ggarrange(p1, p1_1, p1_2, p2, p2_1, p2_2, p3, p3_1, p3_2, p4, p4_1, p4_2, nrow = 4)
#ggarrange(p3, p4, p1, p2, p3_1, p4_1, p1_1, p2_1, p3_2, p4_2, p1_2, p2_2, nrow = 3, heights = c(2,1,1))
ggarrange(p4, p2, nrow = 1)
ggarrange(p4_1, p2_1, p4_2, p2_2, nrow = 2)
#, width=0.7, fill="steelblue"
```

::::: panel-tabset
### Myotis vivesi

```{r, fig.width = 17, fig.height = 13}
#| message: false
#| warning: false

all_species = colnames(gene_loss_full)
gene_loss_viv_table = gene_loss_full[gene_loss_full$HLmyoViv1 %notin% c("I", "FI") & gene_loss_full$HLmyoViv5 == "L",]# & gene_loss_full$HLmyoViv3 == "L" & gene_loss_full$HLmyoViv5 == "L",]
gene_loss_lep_table = gene_loss_full[gene_loss_full$HLnocLep1 %notin% c("I", "FI") & gene_loss_full$HLnocLep2 == "L",]#, "UL"),]

gene_L_UL_viv_table = gene_loss_full[gene_loss_full$HLmyoViv1 %notin% c("I", "FI") & gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]# & gene_loss_full$HLmyoViv3 %in% c("L", "UL") & gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]
gene_L_UL_lep_table = gene_loss_full[gene_loss_full$HLnocLep1 %notin% c("I", "FI") & gene_loss_full$HLnocLep2 %in% c("L", "UL"),]#, "UL"),]
gene_common_L_UL_viv_lep = gene_loss_full[gene_loss_full$HLnocLep1 %notin% c("I", "FI") & gene_loss_full$HLnocLep2 %in% c("L", "UL") & gene_loss_full$HLmyoViv1 %notin% c("I", "FI") & gene_loss_full$HLmyoViv5 %in% c("L", "UL"),]

losses_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_loss_viv_table)))
losses_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_loss_lep_table)))

L_UL_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_L_UL_viv_table)))
L_UL_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_L_UL_lep_table)))

common_L_UL_viv_lep = data.frame(row.names = c("node_number", rownames(gene_common_L_UL_viv_lep)))

for (label1 in all_species){
  for (label2 in all_species) {
    label_in_tree = paste0(label1, "_", label2)
    if (label_in_tree %in% c(tree$node.label)) {
      node_number = MRCA(tree, label_in_tree)
      tips = tree$tip.label[unlist(Descendants(tree, node_number, type = c("tips")))]
      if ("HLmyoViv5" %in% tips) {
        if (length(tips) < 4) {
          losses_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_viv_table) %in% 
                                                            c(rownames(gene_loss_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
          L_UL_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_viv_table) %in% 
                                                            c(rownames(gene_L_UL_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
        }
        else {
          losses_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_loss_viv_table) %in% 
                                                            rownames(gene_loss_viv_table[(rowMeans(gene_loss_viv_table[,tips[tips != "HLmyoViv5"]] == "I") +
                                                                                            rowMeans(gene_loss_viv_table[,tips[tips != "HLmyoViv5"]] == "FI")) >= 0.9,])))
          L_UL_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_L_UL_viv_table) %in% 
                                                            rownames(gene_L_UL_viv_table[(rowMeans(gene_L_UL_viv_table[,tips[tips != "HLmyoViv5"]] == "I") +
                                                                                            rowMeans(gene_L_UL_viv_table[,tips[tips != "HLmyoViv5"]] == "FI")) >= 0.9,])))
          common_L_UL_viv_lep[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_common_L_UL_viv_lep) %in% 
                                                            rownames(gene_common_L_UL_viv_lep[(rowMeans(gene_common_L_UL_viv_lep[,tips[tips %notin% c("HLmyoViv5", "HLnocLep2")]] == "I") +
                                                                                            rowMeans(gene_common_L_UL_viv_lep[,tips[tips %notin% c("HLmyoViv5", "HLnocLep2")]] == "FI")) >= 0.5,])))
        }
      }
      if ("HLnocLep2" %in% tips) {
        if (length(tips) < 3) {
          losses_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_lep_table) %in% 
                                                            c(rownames(gene_loss_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
          L_UL_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_lep_table) %in% 
                                                            c(rownames(gene_L_UL_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x %in% c("FI", "I")))))))
        }
        else {
          losses_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_loss_lep_table) %in% 
                                                            rownames(gene_loss_lep_table[(rowMeans(gene_loss_lep_table[,tips[tips != "HLnocLep2"]] == "I") +
                                                                                            rowMeans(gene_loss_lep_table[,tips[tips != "HLnocLep2"]] == "FI")) >= 0.9,])))
          L_UL_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_L_UL_lep_table) %in% 
                                                            rownames(gene_L_UL_lep_table[(rowMeans(gene_L_UL_lep_table[,tips[tips != "HLnocLep2"]] == "I") +
                                                                                            rowMeans(gene_L_UL_lep_table[,tips[tips != "HLnocLep2"]] == "FI")) >= 0.9,])))
        }
      }
    }
  }
}
library(wrapr)
losses_by_background_viv = losses_by_background_viv[-1,order(as.numeric(losses_by_background_viv["node_number",]), decreasing = TRUE)]
losses_by_background_lep = losses_by_background_lep[-c(1),order(as.numeric(losses_by_background_lep["node_number",]), decreasing = TRUE)]

L_UL_by_background_viv = L_UL_by_background_viv[-c(1),order(as.numeric(L_UL_by_background_viv["node_number",]), decreasing = TRUE)]
L_UL_by_background_lep = L_UL_by_background_lep[-c(1),order(as.numeric(L_UL_by_background_lep["node_number",]), decreasing = TRUE)]
common_L_UL_viv_lep = common_L_UL_viv_lep[-c(1),order(as.numeric(common_L_UL_viv_lep["node_number",]), decreasing = TRUE)]
strsplit(rownames(common_L_UL_viv_lep[common_L_UL_viv_lep$HLmyzAur1_HLnycThe1A == 1,]), "#") %>% lapply(function(x) x[2]) %>% unlist
common_L_UL_viv_lep = common_L_UL_viv_lep[common_L_UL_viv_lep$HLmyzAur1_HLnycThe1A == 1,]
common_L_UL_all_states = gene_common_L_UL_viv_lep[rownames(common_L_UL_viv_lep), colnames(gene_common_L_UL_viv_lep) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
species = synonyms_df[order(match(synonyms_df$old, colnames(common_L_UL_all_states))),]
colnames(common_L_UL_all_states) = species[species$old %in% colnames(common_L_UL_all_states),]$new
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
tree_common = ggplot(renamed_tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE, fontface = "italic", size=7)
rownames(common_L_UL_all_states) = strsplit(rownames(common_L_UL_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
common_L_UL_all_states = common_L_UL_all_states[rownames(common_L_UL_all_states) != "RAET1E",]
p1 = gheatmap(tree_common, as.data.frame(t(common_L_UL_all_states)), offset=20, width = 3, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text=element_text(size=25), axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1) + vexpand(-1)#+
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=75, width = .6, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text=element_text(size=20), axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1)
```

```{r, fig.width = 14, fig.height = 13}
#| message: false
#| warning: false
losses_by_background_viv = losses_by_background_viv[losses_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
losses_by_background_viv = losses_by_background_viv[order(losses_by_background_viv[,2]),]
losses_by_background_viv = losses_by_background_viv[losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
losses_viv_all_states = gene_loss_viv_table[rownames(losses_by_background_viv), colnames(gene_loss_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
colnames(losses_viv_all_states) = species[species$old %in% colnames(losses_viv_all_states),]$new
#losses_viv_all_states <- losses_viv_all_states[, tree$tip.label]
#gene_symbols = select(org.Hs.eg.db, rownames(losses_viv_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#rownames(losses_viv_all_states) = gene_symbols$SYMBOL
#losses_viv_all_states_for_heat <- melt(as.matrix(losses_viv_all_states))
#colnames(losses_viv_all_states_for_heat) <- c("y", "x", "value")
#ggplot(losses_viv_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile(color = "black") +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))
tree$label[MRCA(tree, "HLnocLep2")] = "background"
tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
tree_viv = ggplot(renamed_tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE, fontface = "italic", size=7)
rownames(losses_viv_all_states) = strsplit(rownames(losses_viv_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
gheatmap(tree_viv, as.data.frame(t(losses_viv_all_states)), offset=6, width = 0.2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
#theme(legend.position="none", axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
  #geom_text(data=as.data.frame(t(losses_viv_all_states)), aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
#df = get_heatmap_column_position(p, by="bottom")
#p + geom_text(data=df, aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false
library(gprofiler2)
enrichment.not_same.myoviv = gost(strsplit(rownames(losses_by_background_viv),"#") %>% lapply(function(x) x[2]) %>% unlist,#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE, custom_bg = strsplit(rownames(gene_loss_full),"#") %>% lapply(function(x) x[2]) %>% unlist)
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)

test_bg = strsplit(rownames(gene_loss_full),"#") %>% lapply(function(x) x[2]) %>% unlist %>% as.data.frame %>% as.matrix
write.csv(file="test_bg_gene_loss.csv", test_bg)
gostplot(enrichment.not_same.myoviv, capped = TRUE, interactive = TRUE)
```

```{r, fig.width = 15, fig.height = 13}
#| message: false
#| warning: false
L_UL_by_background_viv = L_UL_by_background_viv[L_UL_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
L_UL_by_background_viv = L_UL_by_background_viv[order(L_UL_by_background_viv[,2]),]
L_UL_by_background_viv = L_UL_by_background_viv[L_UL_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
L_UL_viv_all_states = gene_L_UL_viv_table[rownames(L_UL_by_background_viv), colnames(gene_L_UL_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
colnames(L_UL_viv_all_states) = species[species$old %in% colnames(L_UL_viv_all_states),]$new
#gene_symbols = select(org.Hs.eg.db, rownames(L_UL_viv_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#rownames(L_UL_viv_all_states) = gene_symbols$SYMBOL
L_UL_viv_all_states_for_heat <- melt(as.matrix(L_UL_viv_all_states))
colnames(L_UL_viv_all_states_for_heat) <- c("y", "x", "value")
#ggplot(L_UL_viv_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile() +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))
rownames(L_UL_viv_all_states) = strsplit(rownames(L_UL_viv_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
L_UL_viv_all_states = L_UL_viv_all_states[rownames(L_UL_viv_all_states) %notin% c("LSS", "CD81", "ODAD2", "DDX4", "FLT4", "CPZ"),]
p1 = gheatmap(tree_viv, as.data.frame(t(L_UL_viv_all_states)), offset=15, width = 1.5, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank(), axis.text=element_text(size=20)) + ggtree::vexpand(0, -1) + vexpand(-1)#+
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=43, width = .3, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text=element_text(size=20), axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false
enrichment.not_same.myoviv = gost(rownames(L_UL_viv_all_states),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE, custom_bg = strsplit(rownames(gene_loss_full),"#") %>% lapply(function(x) x[2]) %>% unlist)
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
gostplot(enrichment.not_same.myoviv, capped = TRUE, interactive = TRUE)
```

### Noctilio leporinus

```{r, fig.width = 15, fig.height = 13}
#| message: false
#| warning: false
losses_by_background_lep = losses_by_background_lep[losses_by_background_lep[,1] != 0,]
#losses_by_background_lep = losses_by_background_lep[order(losses_by_background_lep[,2]),]
losses_by_background_lep = losses_by_background_lep[losses_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
losses_lep_all_states = gene_loss_lep_table[rownames(losses_by_background_lep), colnames(gene_loss_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
colnames(losses_lep_all_states) = species[species$old %in% colnames(losses_lep_all_states),]$new
#gene_symbols = select(org.Hs.eg.db, rownames(losses_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#gene_symbols = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]
#rownames(losses_lep_all_states) = gene_symbols$SYMBOL
losses_lep_all_states_for_heat <- melt(as.matrix(losses_lep_all_states))
colnames(losses_lep_all_states_for_heat) <- c("y", "x", "value")
#ggplot(losses_lep_all_states_for_heat, aes(x = x, y = y, fill = value)) +
#  geom_tile() +
#  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") +
#  theme(axis.text.x=element_text(angle = 90, vjust = 1))
#tree_plot = ggplot(tree, aes(color=tree$label)) + scale_color_manual(values=c("foreground"="#d1182a", "background"="#555555")) + 
#  geom_tree() + theme_tree() + geom_tiplab(align=TRUE)
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv5")] = "background"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
tree_lep = ggplot(renamed_tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE, fontface = "italic", size=7)
rownames(losses_lep_all_states) = strsplit(rownames(losses_lep_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
#losses_lep_all_states = losses_lep_all_states[rownames(losses_lep_all_states) %notin% c("CCDC158", "CRTAM", "A4GNT", "EIF4E1B", "ZNF446", "CD1A", "ANKHD1", "CA13", "NLRC5", "TRAJ32"),]
gheatmap(tree_lep, as.data.frame(t(losses_lep_all_states)), offset=6, width = 1.4, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
  #geom_text(data=as.data.frame(t(losses_viv_all_states)), aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
#df = get_heatmap_column_position(p, by="bottom")
#p + geom_text(data=df, aes(x, y, label=label), nudge_y=-1, angle=45, inherit.aes=FALSE)
```

A4GNT - GI tract mucus LPO - looks very lost, many functions OXGR1, B3GNT4 -\> deafness SERPINB3, 4 -\> reduced inflammation

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false
enrichment.not_same.noclep = gost(rownames(losses_lep_all_states),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE, custom_bg = strsplit(rownames(gene_loss_full),"#") %>% lapply(function(x) x[2]) %>% unlist)
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
#gostplot(enrichment.not_same.noclep, capped = TRUE, interactive = TRUE)
```

```{r, fig.width = 20, fig.height = 13}
#| message: false
#| warning: false
L_UL_by_background_lep = L_UL_by_background_lep[L_UL_by_background_lep[,1] != 0,]
#L_UL_by_background_lep = L_UL_by_background_lep[order(L_UL_by_background_lep[,2]),]
L_UL_by_background_lep = L_UL_by_background_lep[L_UL_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
L_UL_lep_all_states = gene_L_UL_lep_table[rownames(L_UL_by_background_lep), colnames(gene_L_UL_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
colnames(L_UL_lep_all_states) = species[species$old %in% colnames(L_UL_lep_all_states),]$new
#gene_symbols = select(org.Hs.eg.db, rownames(L_UL_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#rownames(L_UL_lep_all_states) = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]$SYMBOL
rownames(L_UL_lep_all_states) = strsplit(rownames(L_UL_lep_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
L_UL_lep_all_states = L_UL_lep_all_states[rownames(L_UL_lep_all_states) %notin% c("ZNF446", "CCDC158", "EIF4E1B", "CA13", "ATN1", "DNAJB13", "SCML1", "SCML2",
                                                                                  "TRBJ2-2", "TRAJ25", "TRAJ32", "ENSG00000288644", "PPP1R13L"),]
p1 = gheatmap(tree_lep, as.data.frame(t(L_UL_lep_all_states)), offset=35, width = 9, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=195, width = .6, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1)
```

QRFP - Hypophagia and Leanness + hyperactivity SELP - platelet activation FUCA2 - glycolipids, glycoproteins PKD2L1 - calcium-regulated nonselective cation channel, sour taste perception; PKD1L3 is also L/UL https://www.pnas.org/doi/10.1073/pnas.0602702103 CARD6 - caspase recruiting domain, activation of the inducible transcription factor NF-kB NLRC5 - member of the caspase recruitment domain-containing NLR family

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false

#c("CD55","LSS","ODAD2","TBC1D8","CD81","IL17RE","NIPAL2","ATP8B3","NARF")

enrichment.not_same.noclep = gost(rownames(L_UL_lep_all_states),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE, custom_bg = strsplit(rownames(gene_loss_full),"#") %>% lapply(function(x) x[2]) %>% unlist)
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
#gostplot(enrichment.not_same.noclep, capped = TRUE, interactive = TRUE)
```

## T2R receptors

```{r, fig.width = 12, fig.height = 12}
#| message: false
#| warning: false
t2r_receptors = rbind(gene_loss_full[grep("TAS1R", rownames(gene_loss_full)),],
                      gene_loss_full[grep("TAS2R", rownames(gene_loss_full)),],
                      gene_loss_full[grep("TRPM5", rownames(gene_loss_full)),],
                      gene_loss_full[grep("PLCB2", rownames(gene_loss_full)),],
                      gene_loss_full[grep("CALHM1", rownames(gene_loss_full)),]) %>% data.frame
t2r_receptors$gene = strsplit(rownames(t2r_receptors),"#") %>% lapply(function(x) x[2]) %>% unlist
#t2r_receptors = t2r_receptors[t2r_receptors$gene %in% c("LRRK2", "TRANK1", "ADGRF4", "CALB1", "CNTNAP3", "LRTM1", "TUNAR", "DISP3", "GRIN2C", "OLIG1", "CAMK2D", "TAAR5"),]
t2r_receptors = t2r_receptors[, colnames(t2r_receptors) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
rownames(t2r_receptors) = t2r_receptors$gene
#gene_symbols = select(org.Hs.eg.db, rownames(L_UL_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
#rownames(L_UL_lep_all_states) = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]$SYMBOL
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
tree_plot = ggplot(tree, aes(color=tree$label)) + scale_color_manual(values=c("focus\nspecies"="#d1182a", "background"="#555555")) + 
  geom_tree() + theme_tree() + geom_tiplab(align=TRUE)
p1 <- gheatmap(tree_plot, as.data.frame(t(t2r_receptors)), offset=5, width = 0.6, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(gene.colors, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)#+
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=20, width = 0.3, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states) +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1)
```

## Duplicated genes

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
gene_dupl_full = read.csv("dupl_genes_with_myoviv5.txt", sep="\t", row.names = 1, header = T) %>% as.data.frame()
gene_dupl_full = gene_dupl_full[,colnames(gene_dupl_full) %notin% c("HLmyoViv2", "HLmyoViv3")]
all_species = colnames(gene_dupl_full)
gene_dupl_viv_table = gene_dupl_full[gene_dupl_full$HLmyoViv1 == "one2many" & gene_dupl_full$HLmyoViv5 == "one2many",]# & gene_dupl_full$HLmyoViv3 == "one2many" & gene_dupl_full$HLmyoViv5 == "one2many",]
gene_dupl_lep_table = gene_dupl_full[gene_dupl_full$HLnocLep1 == "one2many" & gene_dupl_full$HLnocLep2 == "one2many",]

dupl_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_dupl_viv_table)))
dupl_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_dupl_lep_table)))

for (label1 in all_species){
  for (label2 in all_species) {
    label_in_tree = paste0(label1, "_", label2)
    if (label_in_tree %in% c(tree$node.label)) {
      node_number = MRCA(tree, label_in_tree)
      tips = tree$tip.label[unlist(Descendants(tree, node_number, type = c("tips")))]
      if ("HLmyoViv5" %in% tips) {
        if (length(tips) < 4) {
          dupl_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_viv_table) %in% 
                                                            c(rownames(gene_dupl_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x == "one2one"))))))
        }
        else {
          dupl_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_dupl_viv_table) %in% 
                                                            rownames(gene_dupl_viv_table[rowMeans(gene_dupl_viv_table[,tips[tips %notin% c("HLmyoViv5")]] == "one2one") >= 0.9 ,])))
        }
      }
      if ("HLnocLep2" %in% tips) {
        if (length(tips) < 3) {
          dupl_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_lep_table) %in% 
                                                            c(rownames(gene_dupl_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x == "one2one"))))))
        }
        else {
          dupl_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_lep_table) %in% 
                                                            rownames(gene_dupl_lep_table[rowMeans(gene_dupl_lep_table[,tips[tips != "HLnocLep2"]] == "one2one") >= 0.9,])))
        }
      }
    }
  }
}
dupl_by_background_viv = dupl_by_background_viv[-c(1),order(as.numeric(dupl_by_background_viv["node_number",]), decreasing = TRUE)]
dupl_by_background_lep = dupl_by_background_lep[-c(1),order(as.numeric(dupl_by_background_lep["node_number",]), decreasing = TRUE)]
dupl.colors = c("blue", "lightblue", "orange", "gray50", "yellow")
dupl.states = c("many2many", "many2one", "one2many", "one2one", "one2zero")
```

```{r, fig.width = 15, fig.height = 12}
#| message: false
#| warning: false
dupl_by_background_viv = dupl_by_background_viv[dupl_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
dupl_by_background_viv = dupl_by_background_viv[order(dupl_by_background_viv[,2]),]
dupl_by_background_viv = dupl_by_background_viv[dupl_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
dupl_viv_all_states = gene_dupl_viv_table[rownames(dupl_by_background_viv), colnames(gene_dupl_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
gene_symbols = select(org.Hs.eg.db, rownames(dupl_viv_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
rownames(dupl_viv_all_states) = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]$SYMBOL
dupl_viv_all_states = dupl_viv_all_states[c("FABP3", "ORMDL2", "UQCRQ", "PEA15", "NDUFB1", "RPL22"),]
tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
tree$label[MRCA(tree, "HLnocLep2")] = "background"
gheatmap(tree_viv, as.data.frame(t(dupl_viv_all_states)), offset=3, width = .2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(dupl.colors, dupl.states), name="dupl state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false
enrichment.dupl.myoviv = gost(rownames(dupl_by_background_viv[dupl_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_viv_table))
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
#gostplot(enrichment.dupl.myoviv, capped = TRUE, interactive = TRUE)
```

```{r, fig.width = 15, fig.height = 12}
#| message: false
#| warning: false
dupl_by_background_lep = dupl_by_background_lep[dupl_by_background_lep[,1] != 0,]
dupl_by_background_lep = dupl_by_background_lep[order(dupl_by_background_lep[,2]),]
dupl_by_background_lep = dupl_by_background_lep[dupl_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
dupl_lep_all_states = gene_dupl_lep_table[rownames(dupl_by_background_lep), colnames(gene_dupl_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
gene_symbols = select(org.Hs.eg.db, rownames(dupl_lep_all_states), c("ENSEMBL", "SYMBOL"), "ENSEMBL") %>% mutate(SYMBOL = coalesce(SYMBOL, ENSEMBL))
rownames(dupl_lep_all_states) = gene_symbols[!duplicated(gene_symbols$ENSEMBL),]$SYMBOL
dupl_lep_all_states = dupl_lep_all_states[c("SELENBP1", "C1GALT1C1", "MMP24OS", "CASP3", "C7orf61"),]
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv3")] = "background"
gheatmap(tree_lep, as.data.frame(t(dupl_lep_all_states)), offset=4, width = .3, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(dupl.colors, dupl.states), name="dupl state") + 
  theme(axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
enrichment.dupl.noclep = gost(rownames(dupl_by_background_lep[dupl_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]),#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_viv_table))
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
#gostplot(enrichment.dupl.noclep, capped = TRUE, interactive = TRUE)
```

## Duplicated genes TOGA2

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
gene_dupl_full = read.csv("toga2_loss/dupl_genes_16072025.txt", sep="\t", row.names = 1, header = T) %>% as.data.frame()
names(gene_dupl_full)[names(gene_dupl_full) == 'HLnocLep2_upd'] <- 'HLnocLep2'
gene_dupl_full = gene_dupl_full[,colnames(gene_dupl_full) %notin% c("HLmyoViv2", "HLmyoViv3")]
all_species = colnames(gene_dupl_full)
gene_dupl_viv_table = gene_dupl_full[gene_dupl_full$HLmyoViv1 == "one2many" & gene_dupl_full$HLmyoViv5 == "one2many",]# & gene_dupl_full$HLmyoViv3 == "one2many" & gene_dupl_full$HLmyoViv5 == "one2many",]
gene_dupl_lep_table = gene_dupl_full[gene_dupl_full$HLnocLep1 == "one2many" & gene_dupl_full$HLnocLep2 == "one2many",]

dupl_by_background_viv = data.frame(row.names = c("node_number", rownames(gene_dupl_viv_table)))
dupl_by_background_lep = data.frame(row.names = c("node_number", rownames(gene_dupl_lep_table)))

for (label1 in all_species){
  for (label2 in all_species) {
    label_in_tree = paste0(label1, "_", label2)
    if (label_in_tree %in% c(tree$node.label)) {
      node_number = MRCA(tree, label_in_tree)
      tips = tree$tip.label[unlist(Descendants(tree, node_number, type = c("tips")))]
      if ("HLmyoViv5" %in% tips) {
        if (length(tips) < 4) {
          dupl_by_background_viv[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_viv_table) %in% 
                                                            c(rownames(gene_dupl_viv_table %>% 
                                                                       filter(if_all(tips[tips != "HLmyoViv5"], 
                                                                                     ~ .x == "one2one"))))))
        }
        else {
          dupl_by_background_viv[,label_in_tree] = c(node_number, 
                                                        c(rownames(gene_dupl_viv_table) %in% 
                                                            rownames(gene_dupl_viv_table[rowMeans(gene_dupl_viv_table[,tips[tips %notin% c("HLmyoViv5")]] == "one2one") >= 0.9 ,])))
        }
      }
      if ("HLnocLep2" %in% tips) {
        if (length(tips) < 3) {
          dupl_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_lep_table) %in% 
                                                            c(rownames(gene_dupl_lep_table %>% 
                                                                       filter(if_all(tips[tips != "HLnocLep2"], 
                                                                                     ~ .x == "one2one"))))))
        }
        else {
          dupl_by_background_lep[,label_in_tree] = c(node_number,
                                                        c(rownames(gene_dupl_lep_table) %in% 
                                                            rownames(gene_dupl_lep_table[rowMeans(gene_dupl_lep_table[,tips[tips != "HLnocLep2"]] == "one2one") >= 0.9,])))
        }
      }
    }
  }
}
dupl_by_background_viv = dupl_by_background_viv[-c(1),order(as.numeric(dupl_by_background_viv["node_number",]), decreasing = TRUE)]
dupl_by_background_lep = dupl_by_background_lep[-c(1),order(as.numeric(dupl_by_background_lep["node_number",]), decreasing = TRUE)]
dupl.colors = c("blue", "lightblue", "orange", "gray50", "yellow")
dupl.states = c("many2many", "many2one", "one2many", "one2one", "one2zero")
```

```{r, fig.width = 15, fig.height = 13}
#| message: false
#| warning: false
dupl_by_background_viv = dupl_by_background_viv[dupl_by_background_viv$HLmyoViv5_HLmyoLuc2 != 0,]
dupl_by_background_viv = dupl_by_background_viv[order(dupl_by_background_viv[,2]),]
dupl_by_background_viv = dupl_by_background_viv[dupl_by_background_viv$HLmyzAur1_HLnycThe1A == 1,]
dupl_viv_all_states = gene_dupl_viv_table[rownames(dupl_by_background_viv), colnames(gene_dupl_viv_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
dupl_viv_all_states = dupl_viv_all_states[,colnames(dupl_viv_all_states) %in% species$old]
colnames(dupl_viv_all_states) = species[species$old %in% colnames(dupl_viv_all_states),]$new
#dupl_viv_all_states = dupl_viv_all_states[c("FABP3", "ORMDL2", "UQCRQ", "PEA15", "NDUFB1", "RPL22"),]
rownames(dupl_viv_all_states) = strsplit(rownames(dupl_viv_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
dupl_viv_all_states = dupl_viv_all_states[rownames(dupl_viv_all_states) %notin% c("SCT", "MED9"),]
tree$label[MRCA(tree, "HLmyoViv5")] = "focus\nspecies"
tree$label[MRCA(tree, "HLnocLep2")] = "background"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
#-SCT, MED9, LCN8, SEMA4F
#rownames(dupl_by_background_viv) = strsplit(rownames(dupl_by_background_viv),"#") %>% lapply(function(x) x[2]) %>% unlist
p1 = gheatmap(tree_viv, as.data.frame(t(dupl_viv_all_states)), offset=10, width = .2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(dupl.colors, dupl.states), name="dupl state") + 
  theme(axis.text = element_text(size=15), axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=15, width = .2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1)
```

```{r, fig.width = 17, fig.height = 12}
#| message: false
#| warning: false
#| eval: false
enrichment.not_same.myoviv = gost(strsplit(rownames(dupl_by_background_viv),"#") %>% lapply(function(x) x[2]) %>% unlist,#[rowMeans(losses_by_background_viv == 1) == 1,]),
                                  #rownames(losses_by_background_viv[(losses_by_background_viv$HLmyzAur1_HLnycThe1A == 1) & 
                                                                      #(losses_by_background_viv$HLmyoViv2_HLmyoLuc2 == 1),]),
                                  evcodes = TRUE)#, custom_bg = rownames(gene_loss_viv_table))
#enrichment.not_same.myoviv = gost(rownames(losses_by_background_viv[rowMeans(losses_by_background_viv == 1) == 1,])[c(1,4,7,9,10,11,13,14,15,19,20)], evcodes = TRUE)
#gostplot(enrichment.not_same.noclep, capped = TRUE, interactive = TRUE)
```

```{r, fig.width = 15, fig.height = 13}
#| message: false
#| warning: false
dupl_by_background_lep = dupl_by_background_lep[dupl_by_background_lep[,1] != 0,]
dupl_by_background_lep = dupl_by_background_lep[order(dupl_by_background_lep[,2]),]
dupl_by_background_lep = dupl_by_background_lep[dupl_by_background_lep$HLmyzAur1_HLnycThe1A == 1,]
dupl_lep_all_states = gene_dupl_lep_table[rownames(dupl_by_background_lep), colnames(gene_dupl_lep_table) %notin% c("HLmyoViv1", "HLmyoViv2", "HLmyoViv3", "HLnocLep1")]
dupl_lep_all_states = dupl_lep_all_states[,colnames(dupl_lep_all_states) %in% species$old]
colnames(dupl_lep_all_states) = species[species$old %in% colnames(dupl_lep_all_states),]$new
rownames(dupl_lep_all_states) = strsplit(rownames(dupl_lep_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
dupl_lep_all_states = dupl_lep_all_states[rownames(dupl_lep_all_states) %notin% c("ALG13", "TSPAN31", "CTXN1"),]
#dupl_lep_all_states = dupl_lep_all_states[c("SELENBP1", "C1GALT1C1", "MMP24OS", "CASP3", "SPACDR"),]
tree$label[MRCA(tree, "HLnocLep2")] = "focus\nspecies"
tree$label[MRCA(tree, "HLmyoViv5")] = "background"
renamed_tree <- rename_taxa(tree, data = synonyms_df, key = "old", value = "new")
#rownames(dupl_lep_all_states) = strsplit(rownames(dupl_lep_all_states),"#") %>% lapply(function(x) x[2]) %>% unlist
p1 = gheatmap(tree_lep, as.data.frame(t(dupl_lep_all_states)), offset=10, width = .2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_manual(values=setNames(dupl.colors, dupl.states), name="dupl state") + 
  theme(axis.text = element_text(size=15), axis.text.x=element_blank()) + ggtree::vexpand(0, -1) + vexpand(-1)
p2 = p1 + new_scale_fill()
gheatmap(p2, table_bats, offset=10, width = .2, color = "black", colnames_angle=90, hjust = 1) +
  scale_fill_continuous(name="Diet code", breaks = diet.states, high = "#132B43", low = "#56B1F7") +
#  scale_fill_distiller() +
  #scale_fill_manual(values=setNames(state.color, gene.states), name="gene state") + 
  theme(axis.text.x=element_blank(), legend.text = element_text(size=15), legend.title = element_text(size=15)) + ggtree::vexpand(0, -1)
```

## Selection screen

::: panel-tabset
### Number of genes under selection

```{r, fig.width = 17, fig.height = 12}
absrel_corr_1_1000 = cbind(read.csv("selection_2/absrel_corr_1_1000.txt", sep = "\t", header = FALSE), V4 = "1_1000")
absrel_corr1001_4000 = cbind(read.csv("selection_2/absrel_corr_1001_4000.txt", sep = "\t", header = FALSE), V4 = "1001_4000")
absrel_corr4001_7000 = cbind(read.csv("selection_2/absrel_corr_4001_7000.txt", sep = "\t", header = FALSE), V4 = "4001_7000")
absrel_corr7001_10000 = cbind(read.csv("selection_2/absrel_corr_7001_10000.txt", sep = "\t", header = FALSE), V4 = "7001_10000")
absrel_corr10001_13000 = cbind(read.csv("selection_2/absrel_corr_10001_13000.txt", sep = "\t", header = FALSE), V4 = "10001_13000")
absrel_corr13001_15000 = cbind(read.csv("selection_2/absrel_corr_13001_15000.txt", sep = "\t", header = FALSE), V4 = "13001_15000")
absrel_corr15001_17000 = cbind(read.csv("selection_2/absrel_corr_15001_17000.txt", sep = "\t", header = FALSE), V4 = "15001_17000")
absrel_corr17001_18205 = cbind(read.csv("selection_2/absrel_corr_17001_18205.txt", sep = "\t", header = FALSE), V4 = "17001_18205")

absrel_corr = rbind(absrel_corr_1_1000, absrel_corr1001_4000, absrel_corr4001_7000, absrel_corr7001_10000, absrel_corr10001_13000,
                    absrel_corr13001_15000, absrel_corr15001_17000, absrel_corr17001_18205)  %>% data.frame
colnames(absrel_corr) = c("transcript", "label", "pval", "batch")
absrel_corr_sig = absrel_corr[absrel_corr$pval <= 0.05,]
absrel_corr_sig_2 = absrel_corr[absrel_corr$pval <= 0.2,]
absrel_corr_sig_abs = data.frame(t(table(absrel_corr_sig$label)))[,2:3]
colnames(absrel_corr_sig_abs) = c("label", "freq")
tree$rate_nodes = absrel_corr_sig_abs$Freq[c(match(tree$node.label, absrel_corr_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate_tips = absrel_corr_sig_abs$Freq[c(match(tree$tip.label, absrel_corr_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate = rep(0, nrow(tree$edge)+1)
for (node in c(tree$node.label, tree$tip.label)) {
  if (node %in% absrel_corr_sig_abs$label){
    node_number = MRCA(tree, node)
    tree$rate[node_number] = absrel_corr_sig_abs[absrel_corr_sig_abs$label == node,]$freq
  }
}

ggtree(tree, aes(color=tree$rate)) +
  scale_color_gradient2(high="red", mid="#555555", low="gray") + 
    geom_tree() + theme_tree() + geom_tiplab()
```

### Enrichment

```{r, fig.width = 17, fig.height = 12}
#|error: false
absrel_corr[c("transctipt2", "gene")] = str_split_fixed(absrel_corr$transcript, '[.]', 2)
absrel_corr_sig[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_sig$transcript, '[.]', 2)
absrel_corr_sig_2[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_sig_2$transcript, '[.]', 2)
noctilio_selection = absrel_corr_sig[absrel_corr_sig$label=="HLnocLep2",]$gene# %>% strsplit(., ".", fixed=TRUE) %>% unlist() %>% .[seq(0, length(.), 2)]
vivesi_selection = absrel_corr_sig[absrel_corr_sig$label == "HLmyoViv3",]$gene# %>% str_split(., "[.]", n=2) %>% unlist() %>% .[seq(0, length(.), 2)]
#background_selection = absrel_corr_sig$gene# %>% strsplit(., ".", fixed=TRUE) %>% unlist() %>% .[seq(0, length(.), 2)]
#background_selection = background_selection[!duplicated(background_selection)]
background_selection = absrel_corr$gene[!duplicated(absrel_corr$gene)]
enrichment.data.myoviv.selection = gost(vivesi_selection, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
enrichment.data.noclep.selection = gost(noctilio_selection, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
```

### List HLnocLep2

```{r}
noclep_selection = absrel_corr_sig[absrel_corr_sig$label =="HLnocLep2",]
noclep_selection = noclep_selection[order(noclep_selection$transcript),]
index_df = table(absrel_corr_sig[absrel_corr_sig$transcript %in% noclep_selection$transcript,]$transcript) %>% t %>% data.frame
noclep_selection$index = index_df[(index_df$Var2 %in% noclep_selection$transcript) & order(index_df$Var2),]$Freq
noclep_selection = noclep_selection[noclep_selection$index == 1,]
#selected_transcripts_full = read.csv("selection_2/selected_transcripts_full.bed", sep = "\t", header = FALSE)
#selected_transcripts_noclep_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection$transcript,]
#write_delim(selected_transcripts_noclep_005, "selection_2/selected_transcripts_noclep_005.bed", delim = '\t')
kable(noclep_selection) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(noclep_selection$gene, evcodes = TRUE, custom_bg = background_selection)
#gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
```

```{r}
noclep_selection_2 = absrel_corr_sig_2[absrel_corr_sig_2$label =="HLnocLep2",]
noclep_selection_2 = noclep_selection_2[order(noclep_selection_2$transcript),]
index_df = table(absrel_corr_sig_2[absrel_corr_sig_2$transcript %in% noclep_selection_2$transcript,]$transcript) %>% t %>% data.frame
noclep_selection_2$index = index_df[(index_df$Var2 %in% noclep_selection_2$transcript) & order(index_df$Var2),]$Freq
#noclep_selection_2 = noclep_selection_2[noclep_selection_2$index == 1,]
#selected_transcripts_noclep_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection_2$transcript,]
#write_delim(selected_transcripts_noclep_02, "selection_2/selected_transcripts_noclep_02.bed", delim = '\t')
kable(noclep_selection_2) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(noclep_selection_2$gene, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
```

Perplexity: D2HGDH is very important for brain but idk if it is relevant BABAM1 - (accurate) DNA damage repair and cell cycle regulation in response to DNA damage AVPR1B is involved in various physiological processes, including stress responses, social behavior, and fluid balance, with its activity mediated by G proteins that stimulate a phosphatidylinositol-calcium second messenger system TACSTD2 (Tumor-associated calcium signal transducer 2) -\> connection to calcium KL (Klotho) is a gene that encodes the α-Klotho protein, primarily expressed in kidney cells, which plays a crucial role in regulating phosphate homeostasis, calcium metabolism, and vitamin D processing GPX3 (Glutathione Peroxidase 3) is an extracellular antioxidant enzyme that protects cells from oxidative damage by catalyzing the reduction of hydrogen peroxide, lipid peroxides, and organic hydroperoxides using glutathione APAF1 - initiates apoptosis HSD17B4 encodes the D-bifunctional protein, a peroxisomal enzyme with two distinct domains that catalyze the second and third steps of fatty acid beta-oxidation. TMC6 (Transmembrane Channel-Like Protein 6) functions as a Gαq-coupled GPCR-like receptor that senses noxious heat in dorsal root ganglion neurons, playing a crucial role in thermosensation and pain perception

FAAH is particularly important in the metabolism of anandamide, an endogenous cannabinoid involved in various physiological processes such as pain modulation, anxiety, and mood regulation - there was something else about pain, need to check SCT plays a crucial role in maintaining water homeostasis, influencing the duodenal environment by regulating secretions in the stomach, pancreas, and liver, and stimulating the production of bicarbonate-rich pancreatic fluids - idk if important

```{r}
#| eval: false
noctilio_selection_ensg = gconvert(noclep_selection$gene, organism = "hsapiens", target="ENSG") %>% as.data.frame
noctilio_selection_ensg = noctilio_selection_ensg[noctilio_selection_ensg$input == noctilio_selection_ensg$name ,]

noctilio_selection_gene_status = data.frame(gene=noctilio_selection_ensg$target, name=noctilio_selection_ensg$input, status=gene_loss_full[noctilio_selection_ensg$target, "HLnocLep2"])
enrichment.data.noclep.I.selection = gost(noctilio_selection_gene_status[noctilio_selection_gene_status$status == "I", 1], evcodes = TRUE, custom_bg = background_selection)
#gostplot(enrichment.data.noclep.I.selection, capped = TRUE, interactive = TRUE)
#enrichment.data.noclep.UL.selection = gost(noctilio_selection_gene_status[noctilio_selection_gene_status$status == "UL", 1], evcodes = TRUE)
#gostplot(enrichment.data.noclep.UL.selection, capped = TRUE, interactive = TRUE)
```

### List HLmyoViv2

```{r}
myoviv_selection = absrel_corr_sig[absrel_corr_sig$label =="HLmyoViv3",]
myoviv_selection = myoviv_selection[order(myoviv_selection$transcript),]
index_df = table(absrel_corr_sig[absrel_corr_sig$transcript %in% myoviv_selection$transcript,]$transcript) %>% t %>% data.frame
myoviv_selection$index = index_df[(index_df$Var2 %in% myoviv_selection$transcript) & order(index_df$Var2),]$Freq
myoviv_selection = myoviv_selection[myoviv_selection$index == 1,]
#selected_transcripts_myoviv_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection$transcript,]
#write_delim(selected_transcripts_myoviv_005, "selection_2/selected_transcripts_myoviv_005.bed", delim = '\t')
kable(myoviv_selection) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(myoviv_selection$gene, evcodes = TRUE, custom_bg = background_selection)
#gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
```

```{r}
myoviv_selection_2 = absrel_corr_sig_2[absrel_corr_sig_2$label =="HLmyoViv3",]
myoviv_selection_2 = myoviv_selection_2[order(myoviv_selection_2$transcript),]
index_df = table(absrel_corr_sig_2[absrel_corr_sig_2$transcript %in% myoviv_selection_2$transcript,]$transcript) %>% t %>% data.frame
myoviv_selection_2$index = index_df[(index_df$Var2 %in% myoviv_selection_2$transcript) & order(index_df$Var2),]$Freq
#myoviv_selection_2 = myoviv_selection_2[myoviv_selection_2$index == 1,]
#selected_transcripts_myoviv_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection_2$transcript,]
#write_delim(selected_transcripts_myoviv_02, "selection_2/selected_transcripts_myoviv_02.bed", delim = '\t')
kable(myoviv_selection_2) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(myoviv_selection_2$gene, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
```

Mostly from Perplexity: UCN3 - if lacking - obesity, diabetes, cardiovascular disease; glucose homeostasis -\> one substitution ETDB and EDTA are paralogs ITPK1 (Inositol-Tetrakisphosphate 1-Kinase) - connection to inositol metabolism as nocLep too NFKBIB (NF-kappa-B inhibitor beta) - connection to necroptosis because of NF-kappa-B necroptosis activaton pathway ERMP1 (Endoplasmic Reticulum Metallopeptidase 1) is a multifunctional protein involved in the unfolded protein response (UPR) and oxidative stress defense

MYOG - muscle-specific transcription factor that plays a crucial role in skeletal muscle development, differentiation, and homeostasis HOXA10 is a transcription factor encoded by the HOXA10 gene, playing a critical role in embryonic development, particularly in uterine formation and genitourinary tract patterning AGER activates multiple signaling pathways, including NF-κB, MAPK, and PKC, leading to the induction of inflammatory cytokines and contributing to cellular stress responses, oxidative damage, and tissue inflammation SIAE negatively modulates immune responses by influencing the sialylation status of cell surface glycoproteins, particularly CD22, which is essential for B cell function and autoimmunity prevention CACNA1F encodes the alpha-1 subunit of the CaV1.4 voltage-gated calcium channel, which plays a crucial role in visual signal transmission by mediating calcium ion influx in photoreceptor cells of the retina.

```{r}
#|eval: false
myotis_selection_ensg = gconvert(myoviv_selection$gene, organism = "hsapiens", target="ENSG") %>% as.data.frame
myotis_selection_ensg = myotis_selection_ensg[myotis_selection_ensg$input == myotis_selection_ensg$name ,]

myotis_selection_gene_status = data.frame(gene=myotis_selection_ensg$target, name=myotis_selection_ensg$input, status=gene_loss_full[myotis_selection_ensg$target, "HLmyoViv2"])
enrichment.data.myoviv.selection = gost(myotis_selection_gene_status[, 1], evcodes = TRUE)#, custom_bg = background_selection)
#enrichment.data.myoviv.I.selection = gost(myotis_selection_gene_status[myotis_selection_gene_status$status == "I", 1], evcodes = TRUE)
#gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
#enrichment.data.myoviv.UL.selection = gost(myotis_selection_gene_status[myotis_selection_gene_status$status == "UL", 1], evcodes = TRUE)
#gostplot(enrichment.data.myoviv.UL.selection, capped = TRUE, interactive = TRUE)
```

### Errorsink

```{r}
absrel_corr_noclep_005_errorsink = read.csv("selection_2/absrel_corr_noclep_005_errorsink.txt", sep = "\t", header = FALSE)
colnames(absrel_corr_noclep_005_errorsink) = c("transcript", "label", "pval")
absrel_corr_noclep_005_errorsink[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_noclep_005_errorsink$transcript, '[.]', 2)
absrel_corr_noclep_005_errorsink = absrel_corr_noclep_005_errorsink[absrel_corr_noclep_005_errorsink$pval <= 0.05,]
absrel_corr_noclep_005_errorsink_selection = absrel_corr_noclep_005_errorsink[absrel_corr_noclep_005_errorsink$label == "HLnocLep2" & order(absrel_corr_noclep_005_errorsink$transcript),]
index_df = table(absrel_corr_noclep_005_errorsink[absrel_corr_noclep_005_errorsink$transcript %in% absrel_corr_noclep_005_errorsink_selection$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_noclep_005_errorsink_selection$index = index_df[(index_df$Var2 %in% absrel_corr_noclep_005_errorsink_selection$transcript) & order(index_df$Var2),]$Freq
absrel_corr_noclep_005_errorsink_selection = absrel_corr_noclep_005_errorsink_selection[absrel_corr_noclep_005_errorsink_selection$index == 1,]
kable(absrel_corr_noclep_005_errorsink_selection) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(absrel_corr_noclep_005_errorsink_selection$gene, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
```

```{r}
absrel_corr_noclep_02_errorsink = read.csv("selection_2/absrel_corr_noclep_02_errorsink.txt", sep = "\t", header = FALSE)
colnames(absrel_corr_noclep_02_errorsink) = c("transcript", "label", "pval")
absrel_corr_noclep_02_errorsink[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_noclep_02_errorsink$transcript, '[.]', 2)
#absrel_corr_noclep_02_errorsink = absrel_corr_noclep_02_errorsink[absrel_corr_noclep_02_errorsink$label == "HLnocLep2" & absrel_corr_noclep_02_errorsink$pval <= 0.2,]
absrel_corr_noclep_02_errorsink = absrel_corr_noclep_02_errorsink[absrel_corr_noclep_02_errorsink$pval <= 0.2,]
absrel_corr_noclep_02_errorsink_selection = absrel_corr_noclep_02_errorsink[absrel_corr_noclep_02_errorsink$label == "HLnocLep2" & order(absrel_corr_noclep_02_errorsink$transcript),]
index_df = table(absrel_corr_noclep_02_errorsink[absrel_corr_noclep_02_errorsink$transcript %in% absrel_corr_noclep_02_errorsink_selection$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_noclep_02_errorsink_selection$index = index_df[(index_df$Var2 %in% absrel_corr_noclep_02_errorsink_selection$transcript) & order(index_df$Var2),]$Freq
#absrel_corr_noclep_02_errorsink_selection = absrel_corr_noclep_02_errorsink_selection[absrel_corr_noclep_02_errorsink_selection$index == 1,]
kable(absrel_corr_noclep_02_errorsink_selection) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(absrel_corr_noclep_02_errorsink_selection$gene, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
```

```{r}
absrel_corr_myoviv_005_errorsink = read.csv("selection_2/absrel_corr_myoviv_005_errorsink.txt", sep = "\t", header = FALSE)
colnames(absrel_corr_myoviv_005_errorsink) = c("transcript", "label", "pval")
absrel_corr_myoviv_005_errorsink[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_myoviv_005_errorsink$transcript, '[.]', 2)
absrel_corr_myoviv_005_errorsink = absrel_corr_myoviv_005_errorsink[absrel_corr_myoviv_005_errorsink$pval <= 0.05,]
absrel_corr_myoviv_005_errorsink_selection = absrel_corr_myoviv_005_errorsink[absrel_corr_myoviv_005_errorsink$label == "HLmyoViv3" & order(absrel_corr_myoviv_005_errorsink$transcript),]
index_df = table(absrel_corr_myoviv_005_errorsink[absrel_corr_myoviv_005_errorsink$transcript %in% absrel_corr_myoviv_005_errorsink_selection$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_myoviv_005_errorsink_selection$index = index_df[(index_df$Var2 %in% absrel_corr_myoviv_005_errorsink_selection$transcript) & order(index_df$Var2),]$Freq
absrel_corr_myoviv_005_errorsink_selection = absrel_corr_myoviv_005_errorsink_selection[absrel_corr_myoviv_005_errorsink_selection$index == 1,]
kable(absrel_corr_myoviv_005_errorsink_selection) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(absrel_corr_myoviv_005_errorsink_selection$gene, evcodes = TRUE, custom_bg = background_selection)
#gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
```

```{r}
absrel_corr_myoviv_02_errorsink = read.csv("selection_2/absrel_corr_myoviv_02_errorsink.txt", sep = "\t", header = FALSE)
colnames(absrel_corr_myoviv_02_errorsink) = c("transcript", "label", "pval")
absrel_corr_myoviv_02_errorsink[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_myoviv_02_errorsink$transcript, '[.]', 2)
#absrel_corr_myoviv_02_errorsink = absrel_corr_myoviv_02_errorsink[absrel_corr_myoviv_02_errorsink$label == "HLmyoViv3" & absrel_corr_myoviv_02_errorsink$pval <= 0.2,]
absrel_corr_myoviv_02_errorsink = absrel_corr_myoviv_02_errorsink[absrel_corr_myoviv_02_errorsink$pval <= 0.2,]
absrel_corr_myoviv_02_errorsink_selection = absrel_corr_myoviv_02_errorsink[absrel_corr_myoviv_02_errorsink$label == "HLmyoViv3" & order(absrel_corr_myoviv_02_errorsink$transcript),]
index_df = table(absrel_corr_myoviv_02_errorsink[absrel_corr_myoviv_02_errorsink$transcript %in% absrel_corr_myoviv_02_errorsink_selection$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_myoviv_02_errorsink_selection$index = index_df[(index_df$Var2 %in% absrel_corr_myoviv_02_errorsink_selection$transcript) & order(index_df$Var2),]$Freq
kable(absrel_corr_myoviv_02_errorsink_selection) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(absrel_corr_myoviv_02_errorsink_selection$gene, evcodes = TRUE, custom_bg = background_selection)
gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
```
:::

## Selection screen TOGA2

::: panel-tabset
### Number of genes under selection

```{r, fig.width = 17, fig.height = 12}
absrel_corr_prank_1_3000 = cbind(read.csv("selection_toga2/absrel_corr_prank_1_3000.txt", sep = "\t", header = FALSE), V4 = "1_3000")
absrel_corr_macse2_1_3000 = cbind(read.csv("selection_toga2/absrel_corr_macse2_1_3000.txt", sep = "\t", header = FALSE), V4 = "1_3000")
absrel_corr_prank_3001_6000 = cbind(read.csv("selection_toga2/absrel_corr_prank_3001_6000.txt", sep = "\t", header = FALSE), V4 = "3001_6000")
absrel_corr_macse2_3001_6000 = cbind(read.csv("selection_toga2/absrel_corr_macse2_3001_6000.txt", sep = "\t", header = FALSE), V4 = "3001_6000")
absrel_corr_prank_6001_9000 = cbind(read.csv("selection_toga2/absrel_corr_prank_6001_9000.txt", sep = "\t", header = FALSE), V4 = "6001_9000")
absrel_corr_macse2_6001_9000 = cbind(read.csv("selection_toga2/absrel_corr_macse2_6001_9000.txt", sep = "\t", header = FALSE), V4 = "6001_9000")
absrel_corr_prank_9001_12000 = cbind(read.csv("selection_toga2/absrel_corr_prank_9001_12000.txt", sep = "\t", header = FALSE), V4 = "9001_12000")
absrel_corr_macse2_9001_12000 = cbind(read.csv("selection_toga2/absrel_corr_macse2_9001_12000.txt", sep = "\t", header = FALSE), V4 = "9001_12000")
absrel_corr_prank_12001_15000 = cbind(read.csv("selection_toga2/absrel_corr_prank_12001_15000.txt", sep = "\t", header = FALSE), V4 = "12001_15000")
absrel_corr_macse2_12001_15000 = cbind(read.csv("selection_toga2/absrel_corr_macse2_12001_15000.txt", sep = "\t", header = FALSE), V4 = "12001_15000")
absrel_corr_prank_15001_18075 = cbind(read.csv("selection_toga2/absrel_corr_prank_15001_18075.txt", sep = "\t", header = FALSE), V4 = "15001_18075")
absrel_corr_macse2_15001_18075 = cbind(read.csv("selection_toga2/absrel_corr_macse2_15001_18075.txt", sep = "\t", header = FALSE), V4 = "15001_18075")

absrel_srv_corr_prank_1_3000 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_1_3000.txt", sep = "\t", header = FALSE), V4 = "1_3000")
absrel_srv_corr_macse2_1_3000 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_1_3000.txt", sep = "\t", header = FALSE), V4 = "1_3000")
absrel_srv_corr_prank_3001_6000 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_3001_6000.txt", sep = "\t", header = FALSE), V4 = "3001_6000")
absrel_srv_corr_macse2_3001_6000 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_3001_6000.txt", sep = "\t", header = FALSE), V4 = "3001_6000")
absrel_srv_corr_prank_6001_9000 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_6001_9000.txt", sep = "\t", header = FALSE), V4 = "6001_9000")
absrel_srv_corr_macse2_6001_9000 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_6001_9000.txt", sep = "\t", header = FALSE), V4 = "6001_9000")
absrel_srv_corr_prank_9001_12000 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_9001_12000.txt", sep = "\t", header = FALSE), V4 = "9001_12000")
absrel_srv_corr_macse2_9001_12000 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_9001_12000.txt", sep = "\t", header = FALSE), V4 = "9001_12000")
absrel_srv_corr_prank_12001_15000 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_12001_15000.txt", sep = "\t", header = FALSE), V4 = "12001_15000")
absrel_srv_corr_macse2_12001_15000 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_12001_15000.txt", sep = "\t", header = FALSE), V4 = "12001_15000")
absrel_srv_corr_prank_15001_18075 = cbind(read.csv("selection_toga2/absrel_srv_corr_prank_15001_18075.txt", sep = "\t", header = FALSE), V4 = "15001_18075")
absrel_srv_corr_macse2_15001_18075 = cbind(read.csv("selection_toga2/absrel_srv_corr_macse2_15001_18075.txt", sep = "\t", header = FALSE), V4 = "15001_18075")

absrel_corr_prank = rbind(absrel_corr_prank_1_3000, absrel_corr_prank_3001_6000, absrel_corr_prank_6001_9000, absrel_corr_prank_9001_12000,
                          absrel_corr_prank_12001_15000, absrel_corr_prank_15001_18075)  %>% data.frame
absrel_corr_macse2 = rbind(absrel_corr_macse2_1_3000, absrel_corr_macse2_3001_6000, absrel_corr_macse2_6001_9000, absrel_corr_macse2_9001_12000,
                           absrel_corr_macse2_12001_15000, absrel_corr_macse2_15001_18075)  %>% data.frame

absrel_srv_corr_prank = rbind(absrel_srv_corr_prank_1_3000, absrel_srv_corr_prank_3001_6000, absrel_srv_corr_prank_6001_9000, absrel_srv_corr_prank_9001_12000,
                              absrel_srv_corr_prank_12001_15000, absrel_srv_corr_prank_15001_18075)  %>% data.frame
absrel_srv_corr_macse2 = rbind(absrel_srv_corr_macse2_1_3000, absrel_srv_corr_macse2_3001_6000, absrel_srv_corr_macse2_6001_9000, absrel_srv_corr_macse2_9001_12000,
                               absrel_srv_corr_macse2_12001_15000, absrel_srv_corr_macse2_15001_18075)  %>% data.frame
colnames(absrel_corr_prank) = colnames(absrel_corr_macse2) = colnames(absrel_srv_corr_prank) = colnames(absrel_srv_corr_macse2) = c("transcript", "label", "pval", "batch")

absrel_corr_prank_sig = absrel_corr_prank[absrel_corr_prank$pval <= 0.05,]
absrel_corr_macse2_sig = absrel_corr_macse2[absrel_corr_macse2$pval <= 0.05,]
absrel_srv_corr_prank_sig = absrel_srv_corr_prank[absrel_srv_corr_prank$pval <= 0.05,]
absrel_srv_corr_macse2_sig = absrel_srv_corr_macse2[absrel_srv_corr_macse2$pval <= 0.05,]

absrel_corr_prank_2 = absrel_corr_prank[absrel_corr_prank$pval <= 0.2,]
absrel_corr_macse2_2 = absrel_corr_macse2[absrel_corr_macse2$pval <= 0.2,]
absrel_srv_corr_prank_2 = absrel_srv_corr_prank[absrel_srv_corr_prank$pval <= 0.2,]
absrel_srv_corr_macse2_2 = absrel_srv_corr_macse2[absrel_srv_corr_macse2$pval <= 0.2,]

absrel_corr_prank_sig_abs = data.frame(t(table(absrel_corr_prank_sig$label)))[,2:3]
absrel_corr_macse2_sig_abs = data.frame(t(table(absrel_corr_macse2_sig$label)))[,2:3]
absrel_srv_corr_prank_sig_abs = data.frame(t(table(absrel_srv_corr_prank_sig$label)))[,2:3]
absrel_srv_corr_macse2_sig_abs = data.frame(t(table(absrel_srv_corr_macse2_sig$label)))[,2:3]

colnames(absrel_corr_prank_sig_abs) = colnames(absrel_corr_macse2_sig_abs) = colnames(absrel_srv_corr_prank_sig_abs) = colnames(absrel_srv_corr_macse2_sig_abs) = c("label", "freq")

tree$rate_nodes_prank = absrel_corr_prank_sig_abs$Freq[c(match(tree$node.label, absrel_corr_prank_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate_nodes_macse2 = absrel_corr_macse2_sig_abs$Freq[c(match(tree$node.label, absrel_corr_macse2_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate_tips_prank = absrel_corr_prank_sig_abs$Freq[c(match(tree$tip.label, absrel_corr_prank_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate_tips_macse2 = absrel_corr_macse2_sig_abs$Freq[c(match(tree$tip.label, absrel_corr_macse2_sig_abs$Var2, nomatch = NA))] %>% replace_na(.,0)
tree$rate_macse2 = tree$rate_prank = rep(0, nrow(tree$edge)+1)
for (node in c(tree$node.label, tree$tip.label)) {
  if (node %in% c(absrel_corr_macse2_sig_abs$label, absrel_corr_prank_sig_abs$label)){
    node_number = MRCA(tree, node)
    tree$rate_prank[node_number] = absrel_corr_prank_sig_abs[absrel_corr_prank_sig_abs$label == node,]$freq
    tree$rate_macse2[node_number] = absrel_corr_macse2_sig_abs[absrel_corr_macse2_sig_abs$label == node,]$freq
  }
}

ggtree(tree, aes(color=tree$rate_prank)) +
  scale_color_gradient2(high="red", mid="#555555", low="gray") + 
    geom_tree() + theme_tree() + geom_tiplab()
ggtree(tree, aes(color=tree$rate_macse2)) +
  scale_color_gradient2(high="red", mid="#555555", low="gray") + 
    geom_tree() + theme_tree() + geom_tiplab()
```

### Enrichment

```{r, fig.width = 17, fig.height = 12}
#|error: false
#absrel_corr_prank
#absrel_corr_macse2
not_i_fi_noclep = rbind(read.csv("srv_HLnocLep2_not_I_FI.txt", sep = "\t", header = FALSE),
                        read.csv("std_HLnocLep2_not_I_FI.txt", sep = "\t", header = FALSE))[,1] %>% str_split_fixed('[#]',3) %>% data.frame
not_i_fi_noclep = not_i_fi_noclep[!duplicated(not_i_fi_noclep$X1),]
not_i_fi_noclep$collapsed = paste0(not_i_fi_noclep$X1, "#", not_i_fi_noclep$X2)
not_i_fi_noclep = not_i_fi_noclep$collapsed
not_i_fi_myoviv = rbind(read.csv("srv_HLmyoViv5_not_I_FI.txt", sep = "\t", header = FALSE),
                        read.csv("std_HLmyoViv5_not_I_FI.txt", sep = "\t", header = FALSE))[,1] %>% str_split_fixed('[#]',3) %>% data.frame
not_i_fi_myoviv = not_i_fi_myoviv[!duplicated(not_i_fi_myoviv$X1),]
not_i_fi_myoviv$collapsed = paste0(not_i_fi_myoviv$X1, "#", not_i_fi_myoviv$X2)
not_i_fi_myoviv = not_i_fi_myoviv$collapsed
absrel_corr = inner_join(absrel_corr_prank, absrel_corr_macse2, by=c("transcript", "label"))
#ggplot(absrel_corr[absrel_corr$label == "HLmyoViv5",], aes(x=pval.x, y=pval.y)) + 
#    geom_point()
absrel_corr_sig = inner_join(absrel_corr_prank_sig, absrel_corr_macse2_sig, by=c("transcript", "label"))

absrel_corr_sig_2 = inner_join(absrel_corr_prank_2, absrel_corr_macse2_2, by=c("transcript", "label"))

absrel_corr[c("transctipt2", "gene")] = str_split_fixed(absrel_corr$transcript, '[#]', 2)
absrel_corr_sig[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_sig$transcript, '[#]', 2)
absrel_corr_sig_2[c("transctipt2", "gene")] = str_split_fixed(absrel_corr_sig_2$transcript, '[#]', 2)
noctilio_selection = absrel_corr_sig[absrel_corr_sig$label=="HLnocLep2",]$gene# %>% strsplit(., ".", fixed=TRUE) %>% unlist() %>% .[seq(0, length(.), 2)]
vivesi_selection = absrel_corr_sig[absrel_corr_sig$label == "HLmyoViv5",]$gene# %>% str_split(., "[.]", n=2) %>% unlist() %>% .[seq(0, length(.), 2)]
#background_selection = absrel_corr_sig$gene# %>% strsplit(., ".", fixed=TRUE) %>% unlist() %>% .[seq(0, length(.), 2)]
#background_selection = background_selection[!duplicated(background_selection)]
#background_selection = absrel_corr$gene[!duplicated(absrel_corr$gene)]
#enrichment.data.myoviv.selection = gost(vivesi_selection, evcodes = TRUE)#, custom_bg = background_selection)
#gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
#enrichment.data.noclep.selection = gost(noctilio_selection, evcodes = TRUE)#, custom_bg = background_selection)
#gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)

absrel_srv_corr = inner_join(absrel_srv_corr_prank, absrel_srv_corr_macse2, by=c("transcript", "label"))
absrel_srv_corr_sig = inner_join(absrel_srv_corr_prank_sig, absrel_srv_corr_macse2_sig, by=c("transcript", "label"))
absrel_srv_corr_sig_2 = inner_join(absrel_srv_corr_prank_2, absrel_srv_corr_macse2_2, by=c("transcript", "label"))
absrel_srv_corr[c("transctipt2", "gene")] = str_split_fixed(absrel_srv_corr$transcript, '[#]', 2)
absrel_srv_corr_sig[c("transctipt2", "gene")] = str_split_fixed(absrel_srv_corr_sig$transcript, '[#]', 2)
absrel_srv_corr_sig_2[c("transctipt2", "gene")] = str_split_fixed(absrel_srv_corr_sig_2$transcript, '[#]', 2)
#selection_sig_overlap_noclep = list(prank_std = absrel_corr_prank_sig[(absrel_corr_prank_sig$label == "HLnocLep2") & 
#                                                                        (absrel_corr_prank_sig$transcript %notin% not_i_fi_noclep),]$transcript,
#                                    macse_std = absrel_corr_macse2_sig[(absrel_corr_macse2_sig$label == "HLnocLep2") & 
#                                                                        (absrel_corr_macse2_sig$transcript %notin% not_i_fi_noclep),]$transcript,
#                                    prank_srv = absrel_srv_corr_prank_sig[(absrel_srv_corr_prank_sig$label == "HLnocLep2") & 
#                                                                        (absrel_srv_corr_prank_sig$transcript %notin% not_i_fi_noclep),]$transcript,
#                                    macse_srv = absrel_srv_corr_macse2_sig[(absrel_srv_corr_macse2_sig$label == "HLnocLep2") & 
#                                                                        (absrel_srv_corr_macse2_sig$transcript %notin% #not_i_fi_noclep),]$transcript)
#selection_sig_overlap_myoviv = list(prank_std = absrel_corr_prank_sig[(absrel_corr_prank_sig$label == "HLmyoViv5") & 
#                                                                        (absrel_corr_prank_sig$transcript %notin% not_i_fi_myoviv),]$transcript,
#                                    macse_std = absrel_corr_macse2_sig[(absrel_corr_macse2_sig$label == "HLmyoViv5") & 
#                                                                        (absrel_corr_macse2_sig$transcript %notin% not_i_fi_myoviv),]$transcript,
#                                    prank_srv = absrel_srv_corr_prank_sig[(absrel_srv_corr_prank_sig$label == "HLmyoViv5") & 
#                                                                        (absrel_srv_corr_prank_sig$transcript %notin% not_i_fi_myoviv),]$transcript,
#                                    macse_srv = absrel_srv_corr_macse2_sig[(absrel_srv_corr_macse2_sig$label == "HLmyoViv5") & 
#                                                                        (absrel_srv_corr_macse2_sig$transcript %notin% not_i_fi_myoviv),]$transcript)
#ggVennDiagram(selection_sig_overlap_noclep) #+ coord_flip()
#ggVennDiagram(selection_sig_overlap_myoviv) #+ coord_flip()
selection_sig_2_overlap_noclep = list(prank_std = absrel_corr_prank_2[(absrel_corr_prank_2$label == "HLnocLep2") & 
                                                                        (absrel_corr_prank_2$transcript %notin% not_i_fi_noclep),]$transcript,
                                    macse_std = absrel_corr_macse2_2[(absrel_corr_macse2_2$label == "HLnocLep2") & 
                                                                        (absrel_corr_macse2_2$transcript %notin% not_i_fi_noclep),]$transcript,
                                    prank_srv = absrel_srv_corr_prank_2[(absrel_srv_corr_prank_2$label == "HLnocLep2") & 
                                                                        (absrel_srv_corr_prank_2$transcript %notin% not_i_fi_noclep),]$transcript,
                                    macse_srv = absrel_srv_corr_macse2_2[(absrel_srv_corr_macse2_2$label == "HLnocLep2") & 
                                                                        (absrel_srv_corr_macse2_2$transcript %notin% not_i_fi_noclep),]$transcript)
selection_sig_2_overlap_myoviv = list(prank_std = absrel_corr_prank_2[(absrel_corr_prank_2$label == "HLmyoViv5") & 
                                                                        (absrel_corr_prank_2$transcript %notin% not_i_fi_myoviv),]$transcript,
                                    macse_std = absrel_corr_macse2_2[(absrel_corr_macse2_2$label == "HLmyoViv5") & 
                                                                        (absrel_corr_macse2_2$transcript %notin% not_i_fi_myoviv),]$transcript,
                                    prank_srv = absrel_srv_corr_prank_2[(absrel_srv_corr_prank_2$label == "HLmyoViv5") & 
                                                                        (absrel_srv_corr_prank_2$transcript %notin% not_i_fi_myoviv),]$transcript,
                                    macse_srv = absrel_srv_corr_macse2_2[(absrel_srv_corr_macse2_2$label == "HLmyoViv5") & 
                                                                        (absrel_srv_corr_macse2_2$transcript %notin% not_i_fi_myoviv),]$transcript)
ggvenn(selection_sig_2_overlap_noclep, fill_color=c("darkblue", "skyblue", "lightgreen", "darkgreen"), show_percentage = F, set_name_size = 10, text_size = 10)
ggvenn(selection_sig_2_overlap_myoviv, fill_color=c("darkblue", "skyblue", "lightgreen", "darkgreen"), show_percentage = F, set_name_size = 10, text_size = 10)
```

### List HLnocLep2

```{r}
noclep_selection = absrel_corr_sig[(absrel_corr_sig$label == "HLnocLep2") & (absrel_corr_sig$transcript %notin% not_i_fi_noclep),]
noclep_selection = noclep_selection[order(noclep_selection$transcript),]
index_df = table(absrel_corr_sig[absrel_corr_sig$transcript %in% noclep_selection$transcript,]$transcript) %>% t %>% data.frame
noclep_selection$index = index_df[(index_df$Var2 %in% noclep_selection$transcript) & order(index_df$Var2),]$Freq
noclep_selection = noclep_selection[noclep_selection$index == 1,]
#selected_transcripts_full = read.csv("selection_2/selected_transcripts_full.bed", sep = "\t", header = FALSE)
#selected_transcripts_noclep_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection$transcript,]
#write_delim(selected_transcripts_noclep_005, "selection_2/selected_transcripts_noclep_005.bed", delim = '\t')
kable(noclep_selection) %>% kable_styling("striped") # 9
#enrichment.data.noclep.selection = gost(noclep_selection$gene, evcodes = TRUE)#, custom_bg = background_selection)
#gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)

noclep_srv_selection = absrel_srv_corr_sig[(absrel_srv_corr_sig$label =="HLnocLep2") & (absrel_srv_corr_sig$transcript %notin% not_i_fi_noclep),]
noclep_srv_selection = noclep_srv_selection[order(noclep_srv_selection$transcript),]
index_df = table(absrel_srv_corr_sig[absrel_srv_corr_sig$transcript %in% noclep_srv_selection$transcript,]$transcript) %>% t %>% data.frame
noclep_srv_selection$index = index_df[(index_df$Var2 %in% noclep_srv_selection$transcript) & order(index_df$Var2),]$Freq
noclep_srv_selection = noclep_srv_selection[noclep_srv_selection$index == 1,]
#selected_transcripts_full = read.csv("selection_2/selected_transcripts_full.bed", sep = "\t", header = FALSE)
#selected_transcripts_noclep_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection$transcript,]
#write_delim(selected_transcripts_noclep_005, "selection_2/selected_transcripts_noclep_005.bed", delim = '\t')
kable(noclep_srv_selection) %>% kable_styling("striped") # 8

absrel_corr_prank_nl = absrel_corr_prank_sig[(absrel_corr_prank_sig$label == "HLmyoViv5") & (absrel_corr_prank_sig$transcript %notin% not_i_fi_myoviv),]
absrel_corr_prank_nl = absrel_corr_prank_nl[order(absrel_corr_prank_nl$transcript),]
index_df = table(absrel_corr_prank_sig[absrel_corr_prank_sig$transcript %in% absrel_corr_prank_nl$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_prank_nl$index = index_df[(index_df$Var2 %in% absrel_corr_prank_nl$transcript) & order(index_df$Var2),]$Freq
absrel_corr_prank_nl = absrel_corr_prank_nl[absrel_corr_prank_nl$index == 1,]

absrel_corr_macse2_nl = absrel_corr_macse2_sig[(absrel_corr_macse2_sig$label == "HLmyoViv5") & (absrel_corr_macse2_sig$transcript %notin% not_i_fi_myoviv),]
absrel_corr_macse2_nl = absrel_corr_macse2_nl[order(absrel_corr_macse2_nl$transcript),]
index_df = table(absrel_corr_macse2_sig[absrel_corr_macse2_sig$transcript %in% absrel_corr_macse2_nl$transcript,]$transcript) %>% t %>% data.frame
absrel_corr_macse2_nl$index = index_df[(index_df$Var2 %in% absrel_corr_macse2_nl$transcript) & order(index_df$Var2),]$Freq
absrel_corr_macse2_nl = absrel_corr_macse2_nl[absrel_corr_macse2_nl$index == 1,]

absrel_srv_corr_prank_nl = absrel_srv_corr_prank_sig[(absrel_srv_corr_prank_sig$label == "HLmyoViv5") & (absrel_srv_corr_prank_sig$transcript %notin% not_i_fi_myoviv),]
absrel_srv_corr_prank_nl = absrel_srv_corr_prank_nl[order(absrel_srv_corr_prank_nl$transcript),]
index_df = table(absrel_srv_corr_prank_sig[absrel_srv_corr_prank_sig$transcript %in% absrel_srv_corr_prank_nl$transcript,]$transcript) %>% t %>% data.frame
absrel_srv_corr_prank_nl$index = index_df[(index_df$Var2 %in% absrel_srv_corr_prank_nl$transcript) & order(index_df$Var2),]$Freq
absrel_srv_corr_prank_nl = absrel_srv_corr_prank_nl[absrel_srv_corr_prank_nl$index == 1,]

absrel_srv_corr_macse2_nl = absrel_srv_corr_macse2_sig[(absrel_srv_corr_macse2_sig$label == "HLmyoViv5") & (absrel_srv_corr_macse2_sig$transcript %notin% not_i_fi_myoviv),]
absrel_srv_corr_macse2_nl = absrel_srv_corr_macse2_nl[order(absrel_srv_corr_macse2_nl$transcript),]
index_df = table(absrel_srv_corr_macse2_sig[absrel_srv_corr_macse2_sig$transcript %in% absrel_srv_corr_macse2_nl$transcript,]$transcript) %>% t %>% data.frame
absrel_srv_corr_macse2_nl$index = index_df[(index_df$Var2 %in% absrel_srv_corr_macse2_nl$transcript) & order(index_df$Var2),]$Freq
absrel_srv_corr_macse2_nl = absrel_srv_corr_macse2_nl[absrel_srv_corr_macse2_nl$index == 1,]

selection_sig_overlap_noclep = list(prank_std = absrel_corr_prank_nl$transcript,
                                    macse_std = absrel_corr_macse2_nl$transcript,
                                    prank_srv = absrel_srv_corr_prank_nl$transcript,
                                    macse_srv = absrel_srv_corr_macse2_nl$transcript)

ggvenn(selection_sig_overlap_noclep, fill_color=c("darkblue", "skyblue", "lightgreen", "darkgreen"), show_percentage = F, set_name_size = 10, text_size = 10)
```

```{r}
noclep_selection_2 = absrel_corr_sig_2[(absrel_corr_sig_2$label =="HLnocLep2") & (absrel_corr_sig_2$transcript %notin% not_i_fi_noclep),]
noclep_selection_2 = noclep_selection_2[order(noclep_selection_2$transcript),]
index_df = table(absrel_corr_sig_2[absrel_corr_sig_2$transcript %in% noclep_selection_2$transcript,]$transcript) %>% t %>% data.frame
noclep_selection_2$index = index_df[(index_df$Var2 %in% noclep_selection_2$transcript) & order(index_df$Var2),]$Freq
#noclep_selection_2 = noclep_selection_2[noclep_selection_2$index == 1,]
#selected_transcripts_noclep_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection_2$transcript,]
#write_delim(selected_transcripts_noclep_02, "selection_2/selected_transcripts_noclep_02.bed", delim = '\t')
noclep_selection_2$dir = paste0("/projects/project-astepanenko/BatSelectionToga2/srv_prank_",noclep_selection_2$batch.x, "/codon_alignments/", noclep_selection_2$transcript, "/", noclep_selection_2$transcript, ".renamed.manual.fa")
kable(noclep_selection_2) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(noclep_selection_2$gene, evcodes = TRUE)#, custom_bg = background_selection)
gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)

noclep_srv_selection_2 = absrel_srv_corr_sig_2[(absrel_srv_corr_sig_2$label =="HLnocLep2") & (absrel_srv_corr_sig_2$transcript %notin% not_i_fi_noclep),]
noclep_srv_selection_2 = noclep_srv_selection_2[order(noclep_srv_selection_2$transcript),]
index_df = table(absrel_srv_corr_sig_2[absrel_srv_corr_sig_2$transcript %in% noclep_srv_selection_2$transcript,]$transcript) %>% t %>% data.frame
noclep_srv_selection_2$index = index_df[(index_df$Var2 %in% noclep_srv_selection_2$transcript) & order(index_df$Var2),]$Freq
#noclep_selection_2 = noclep_selection_2[noclep_selection_2$index == 1,]
#selected_transcripts_noclep_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% noclep_selection_2$transcript,]
#write_delim(selected_transcripts_noclep_02, "selection_2/selected_transcripts_noclep_02.bed", delim = '\t')
noclep_srv_selection_2$dir = paste0("/projects/project-astepanenko/BatSelectionToga2/srv_prank_",noclep_srv_selection_2$batch.x, "/codon_alignments/", noclep_srv_selection_2$transcript, "/", noclep_srv_selection_2$transcript, ".renamed.manual.fa")
kable(noclep_srv_selection_2) %>% kable_styling("striped")
enrichment.data.noclep.selection = gost(noclep_srv_selection_2$gene, evcodes = TRUE)#, custom_bg = background_selection)
#gostplot(enrichment.data.noclep.selection, capped = TRUE, interactive = TRUE)
#print(as.data.frame(noclep_selection_2[noclep_selection_2$transcript %notin% noclep_srv_selection_2$transcript, "dir"]), row.names=F)
```

### List HLmyoViv5

```{r}
myoviv_selection = absrel_corr_sig[(absrel_corr_sig$label =="HLmyoViv5") & (absrel_corr_sig$transcript %notin% not_i_fi_myoviv),]
myoviv_selection = myoviv_selection[order(myoviv_selection$transcript),]
index_df = table(absrel_corr_sig[absrel_corr_sig$transcript %in% myoviv_selection$transcript,]$transcript) %>% t %>% data.frame
myoviv_selection$index = index_df[(index_df$Var2 %in% myoviv_selection$transcript) & order(index_df$Var2),]$Freq
myoviv_selection = myoviv_selection[myoviv_selection$index == 1,]
#selected_transcripts_myoviv_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection$transcript,]
#write_delim(selected_transcripts_myoviv_005, "selection_2/selected_transcripts_myoviv_005.bed", delim = '\t')	0.00008
kable(myoviv_selection) %>% kable_styling("striped")
#enrichment.data.myoviv.selection = gost(myoviv_selection$gene, evcodes = TRUE)#, custom_bg = background_selection)
#gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)

myoviv_srv_selection = absrel_srv_corr_sig[(absrel_srv_corr_sig$label =="HLmyoViv5") & (absrel_srv_corr_sig$transcript %notin% not_i_fi_myoviv),]
myoviv_srv_selection = myoviv_srv_selection[order(myoviv_srv_selection$transcript),]
index_df = table(absrel_srv_corr_sig[absrel_srv_corr_sig$transcript %in% myoviv_srv_selection$transcript,]$transcript) %>% t %>% data.frame
myoviv_srv_selection$index = index_df[(index_df$Var2 %in% myoviv_srv_selection$transcript) & order(index_df$Var2),]$Freq
myoviv_srv_selection = myoviv_srv_selection[myoviv_srv_selection$index == 1,]
#selected_transcripts_myoviv_005 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection$transcript,]
#write_delim(selected_transcripts_myoviv_005, "selection_2/selected_transcripts_myoviv_005.bed", delim = '\t')
kable(myoviv_srv_selection) %>% kable_styling("striped")
```

```{r}
myoviv_selection_2 = absrel_corr_sig_2[(absrel_corr_sig_2$label =="HLmyoViv5") & (absrel_corr_sig_2$transcript %notin% not_i_fi_myoviv),]
myoviv_selection_2 = myoviv_selection_2[order(myoviv_selection_2$transcript),]
index_df = table(absrel_corr_sig_2[absrel_corr_sig_2$transcript %in% myoviv_selection_2$transcript,]$transcript) %>% t %>% data.frame
myoviv_selection_2$index = index_df[(index_df$Var2 %in% myoviv_selection_2$transcript) & order(index_df$Var2),]$Freq
myoviv_selection_2$dir = paste0("/projects/project-astepanenko/BatSelectionToga2/srv_prank_",myoviv_selection_2$batch.x, "/codon_alignments/", myoviv_selection_2$transcript, "/", myoviv_selection_2$transcript, ".renamed.manual.fa")
#myoviv_selection_2 = myoviv_selection_2[myoviv_selection_2$index == 1,]
#selected_transcripts_myoviv_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection_2$transcript,]
#write_delim(selected_transcripts_myoviv_02, "selection_2/selected_transcripts_myoviv_02.bed", delim = '\t')
kable(myoviv_selection_2) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(myoviv_selection_2$gene, evcodes = TRUE)#, custom_bg = background_selection)
gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)

myoviv_srv_selection_2 = absrel_srv_corr_sig_2[(absrel_srv_corr_sig_2$label =="HLmyoViv5") & (absrel_srv_corr_sig_2$transcript %notin% not_i_fi_myoviv),]
myoviv_srv_selection_2 = myoviv_srv_selection_2[order(myoviv_srv_selection_2$transcript),]
index_df = table(absrel_srv_corr_sig_2[absrel_srv_corr_sig_2$transcript %in% myoviv_srv_selection_2$transcript,]$transcript) %>% t %>% data.frame
myoviv_srv_selection_2$index = index_df[(index_df$Var2 %in% myoviv_srv_selection_2$transcript) & order(index_df$Var2),]$Freq
myoviv_srv_selection_2$dir = paste0("/projects/project-astepanenko/BatSelectionToga2/srv_prank_",myoviv_srv_selection_2$batch.x, "/codon_alignments/", myoviv_srv_selection_2$transcript, "/", myoviv_srv_selection_2$transcript, ".renamed.manual.fa")
#myoviv_selection_2 = myoviv_selection_2[myoviv_selection_2$index == 1,]
#selected_transcripts_myoviv_02 = selected_transcripts_full[selected_transcripts_full$V4 %in% myoviv_selection_2$transcript,]
#write_delim(selected_transcripts_myoviv_02, "selection_2/selected_transcripts_myoviv_02.bed", delim = '\t')
kable(myoviv_srv_selection_2) %>% kable_styling("striped")
enrichment.data.myoviv.selection = gost(myoviv_srv_selection_2$gene, evcodes = TRUE)#, custom_bg = background_selection)
gostplot(enrichment.data.myoviv.selection, capped = TRUE, interactive = TRUE)
selection_screen <- list(noclep_lax = noclep_selection_2$gene,
                         noclep_lax_srv = noclep_srv_selection_2$gene,
                         myoviv_lax = myoviv_selection_2$gene,
                         myoviv_lax_srv = myoviv_srv_selection_2$gene)
selection_screen_noclep <- list(noclep_lax = noclep_selection_2$gene,
                                noclep_lax_srv = noclep_srv_selection_2$gene)
selection_screen_myoviv <- list(myoviv_lax = myoviv_selection_2$gene,
                                myoviv_lax_srv = myoviv_srv_selection_2$gene)
selection_screen_noclep_strict <- list(noclep_strict = noclep_selection$gene,
                                       noclep_strict_srv = noclep_srv_selection$gene)
selection_screen_myoviv_strict <- list(myoviv_strict = myoviv_selection$gene,
                                       myoviv_strict_srv = myoviv_srv_selection$gene)
ggVennDiagram(selection_screen) + scale_x_continuous(expand = expansion(mult = .3))
ggVennDiagram(selection_screen_noclep) + coord_flip()# + scale_x_continuous(expand = expansion(mult = .2))
ggVennDiagram(selection_screen_myoviv) + coord_flip()# + scale_x_continuous(expand = expansion(mult = .3))
ggVennDiagram(selection_screen_noclep_strict) + coord_flip()# + scale_x_continuous(expand = expansion(mult = .2))
ggVennDiagram(selection_screen_myoviv_strict) + coord_flip()# + scale_x_continuous(expand = expansion(mult = .3))
```
:::
:::::
